### 2024-09-13 sample-sigconf.tex
chore: put the outline

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{xx.xxx/xxx_x}

% ISBN
\acmISBN{979-8-4007-0629-5/25/03}

%Conference
\acmConference[SAC'25]{ACM SAC Conference}{March 31 –April 4, 2025}{Sicily, Italy}
\acmYear{2025}
\copyrightyear{2025}

\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\begin{document}
\title{Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Full Paper}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

\renewcommand{\shorttitle}{SIG Proceedings Paper in LaTeX Format}

\author{Ben Trovato}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \country{USA}
  \postcode{43017-6221}  
}
\email{trovato@corporation.com}

\author{G.K.M. Tobin}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \country{USA}
  \postcode{43017-6221}  
}
\email{webmaster@marysville-ohio.com}

\author{Lars Th{\o}rv{\"a}ld}
\authornote{This author is the
  one who did all the really hard work.}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla} 
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}
\author{Aparna Patel} 
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh} 
 \state{Arunachal Pradesh}
 \country{India}}
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu} 
  \state{Beijing Shi}
  \country{China}
}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas} 
  \country{USA}
  \postcode{78229}}  
\email{cpalmer@prl.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
  Multi-Agent Reinforcement Learning (MARL) is gaining popularity as a powerful framework for training agents to collaborate and compete in complex environments. However, MARL introduces unique challenges, such as non-stationarity and partial observability, that complicate the training process.  
  While centralized training methods can address some of these challenges, they often face scalability limitations as the number of agents grows. This paper investigates the effectiveness of various neighbor-based decentralized training strategies as a viable alternative to centralized training. We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods in a custom multi-agent environment and compare their performance against centralized training. Our results show that neighbor-based methods can achieve comparable performance to centralized training while offering improved scalability and communication efficiency. 
  We discuss the trade-offs between these methods and provide insights into their applicability in different scenarios.
  %% More -- add the fact that this make it possible to train agents in a decentralized manner, which is more realistic and scalable than centralized training.
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}
\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}

### 2024-09-13 sample-src.tex
chore: put the outline

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{xx.xxx/xxx_x}

% ISBN
\acmISBN{979-8-4007-0629-5/25/03}

%Conference
\acmConference[SAC'25]{ACM SAC Conference}{March 31 –April 4, 2025}{Sicily, Italy}
\acmYear{2025}
\copyrightyear{2025}

\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\begin{document}
% title should have "Student Research Abstract"
% title should have "Student Research Abstract"
% title should have "Student Research Abstract"
\title{Student Research Abstract: Title of Your Abstract}
% title should have "Student Research Abstract"
% title should have "Student Research Abstract"
% title should have "Student Research Abstract"

%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Ben Trovato}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \country{USA}
  \postcode{43017-6221}
}
\email{trovato@corporation.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\section*{PROBLEM AND MOTIVATION}
The student research abstract (SRA) will be published both in the
printed proceedings of ACM SAC and later in ACM digital
library. The proceedings are the records of the conference. To do
this, we ask that student authors follow some simple guidelines. In
essence, we ask you to make your research abstract look exactly
like this document. The easiest way to do this is simply to
download a template from the website of ACM SAC, and replace
the content with your own material, which includes \emph{the innovation
behind the proposed research idea and the applicability of
anticipated results to real-world problems; the problem being
investigated; the proposed solution and research methodology;
and sample preliminary results of the work.}

\section*{BACKGROUND AND RELATED WORK}
All material on each page should fit within a rectangle of 18 x
23.5 cm (7" x 9.25"), centered on the page, beginning 2.54 cm
(1") from the top of the page and ending with 2.54 cm (1") from
the bottom. The right and left margins should be 1.9 cm (.75").
The text should be in two 8.45 cm (3.33") columns with a .83 cm
(.33") gutter.

\section*{APPROACH AND UNIQUENESS}
\subsection*{Normal or Body Text}
Please use a 9-point Times Roman font, or other Roman font with
serifs, as close as possible in appearance to Times Roman in
which these guidelines have been set. The goal is to have a 9-
point text, as you see here. Please use sans-serif or nonproportional
fonts only for special purposes, such as
distinguishing source code text. If Times Roman is not available,
try the font named Computer Modern Roman. On a Macintosh,
use the font named Times. Right margins should be justified, not
ragged.

\subsection*{Title and Authors}
The title (Helvetica 18-point bold), authors' names (Helvetica 12-
point) and affiliations (Helvetica 10-point) run across the full
width of the page - one column wide. The title should start with
"Student Research Abstract: ". We also recommend e-mail
address (Helvetica 12-point). See the top of this page for example.

\subsection*{Subsequent Pages}
For pages other than the first page, start at the top of the page, and
continue in double-column format. The two columns on the last
page should be as close to equal length as possible.

\begin{table}[h]
\caption{Table captions should be placed above the table}
\begin{tabular}{|c|c|c|c|}
\hline
Graphics & Top & In-between & Bottom \\
\hline
Tables & End & Last & First \\
\hline
Figures & Good & Similar & Very well \\
\hline
\end{tabular}
\end{table}

\begin{figure}
\includegraphics{fly}
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\includegraphics[height=1in, width=1in]{fly}
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

\subsection*{References and Citations}
Footnotes should be Times New Roman 9-point, and justified to
the full width of the column.

Use the standard Communications of the ACM format for
references - that is, a numbered list at the end of the article,
ordered alphabetically by first author, and referenced by numbers
in brackets \cite{Smith10}. See the examples of citations at the end of this
document. Within this template file, use the style named
references for the text of your citation.

The references are also in 9 pt., but that section (see Section 7) is
ragged right. References should be published materials accessible
to the public. Internal technical reports may be cited only if they
are easily accessible (i.e. you can give the address to obtain the
report within your citation) and may be obtained by any reader.
Proprietary information may not be cited. Private communications
should be acknowledged, not referenced (e.g., "[Robertson,
personal communication]").

A couple of citations with DOIs: \cite{2004:ITE:1009386.1010128,
  Kirschmer:2010:AEI:1958016.1958018}.

Online citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

\subsection*{Page Numbering, Headers and Footers}
Do not include headers, footers or page numbers in your
submission. These will be added when the publications are
assembled.

\section*{RESULTS AND CONTRIBUTIONS}
Place Tables/Figures/Images in text as close to the reference as
possible (see Figure 1). It may extend across both columns to a
maximum width of 17.78 cm (7").

Captions should be Times New Roman 9-point bold. They should
be numbered (e.g., "Table 1" or "Figure 2"), please note that the
word for Table and Figure are spelled out. Figure's captions should be centered beneath the image or picture, and Table captions should be centered above the table body.

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}

### 2024-09-13 samplebody-conf.tex
chore: put the outline

\section{Introduction}
\begin{itemize}
\item Highlight the growing importance of MARL and its applications.
\item Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
\item Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
\item Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
\item State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
\end{itemize}

\section{Background}
\begin{itemize}
\item Introduce Multi-Agent Reinforcement Learning (MARL) and its specific challenges.
\item Provide a formalization (networked agents?) and explain the key concepts: joint action space, shared reward, partial observability, and credit assignment.
\item Explain different MARL training schemes: centralized training (CTCE, CTDE), distributed training (DTDE).
\end{itemize}

\section{Neighboring-Based Distributed Learning Strategies}
\begin{itemize}
\item Provide a detailed explanation of each neighbor-based method:
\begin{itemize}
\item \textbf{Independent learners:} Emphasize its simplicity and scalability but highlight its vulnerability to non-stationarity.
\item \textbf{NN-Averaging:} Describe the weight averaging process, discuss the influence of neighbor selection and averaging frequency, and mention weighted averaging variations.
\item \textbf{NN-Consensus:} Explain the selection of the best-performing network and its potential benefits and drawbacks.
\item \textbf{Experience Sharing:} Detail how agents share experiences, discuss asynchronous vs. synchronous sharing, and highlight its advantages in sparse interaction environments.
\end{itemize}
\end{itemize}

\section{Experimental Setup}
\begin{itemize}
\item Introduce the custom "collect the items" multi-agent environment:
\begin{itemize}
\item Describe the environment's dynamics, agent goals, and challenges.
\item Specify the action space (continuous and discrete) and observation space design.
\item Explain the reward structure, emphasizing the components that encourage cooperation.
\end{itemize}
\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
\item Define the evaluation metrics: average episode length and average reward.
\end{itemize}

\section{Results and Evaluation}
\begin{itemize}
\item \textbf{Performance comparison:}
\begin{itemize}
\item Present the results of each distributed strategy against the centralized training baseline.
\item Use graphs and statistical analysis to compare the average episode length and average reward.
\item Highlight which neighbor-based methods perform comparably to centralized training.
\end{itemize}
\item \textbf{Scalability analysis:}
\begin{itemize}
\item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
\item Show how each method scales with the increasing complexity, using appropriate visualizations.
\item Discuss the implications of using pre-trained models with a larger number of agents.
\end{itemize}
\item \textbf{Communication overhead analysis:}
\begin{itemize}
\item Quantify the amount of information exchange for each strategy.
\item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
\item Discuss the trade-offs between performance and communication efficiency.
\item Mention potential techniques for reducing communication overhead.
\end{itemize}
\end{itemize}

\section{Conclusion}
\begin{itemize}
\item Summarize the key findings of the paper.
\item Emphasize the viability of neighbor-based methods as alternatives to centralized training in MARL.
\item Discuss the trade-offs observed in terms of performance, scalability, and communication overhead.
\item Suggest potential directions for future research, such as exploring hybrid approaches or more advanced communication protocols.
\end{itemize}

### 2024-09-13 paper-2024-sac-marl-neighbouring-strategies.tex
chore: remove useless files

--- 2024-09-13 sample-sigconf.tex
@@
 
-\input{samplebody-conf}
+\section{Introduction}
+\begin{itemize}
+\item Highlight the growing importance of MARL and its applications.
+\item Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
+\item Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
+\item Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
+\item State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
+\end{itemize}
+
+\section{Background}
+\begin{itemize}
+\item Introduce Multi-Agent Reinforcement Learning (MARL) and its specific challenges.
+\item Provide a formalization (networked agents?) and explain the key concepts: joint action space, shared reward, partial observability, and credit assignment.
+\item Explain different MARL training schemes: centralized training (CTCE, CTDE), distributed training (DTDE).
+\end{itemize}
+
+\section{Neighboring-Based Distributed Learning Strategies}
+\begin{itemize}
+\item Provide a detailed explanation of each neighbor-based method:
+\begin{itemize}
+\item \textbf{Independent learners:} Emphasize its simplicity and scalability but highlight its vulnerability to non-stationarity.
+\item \textbf{NN-Averaging:} Describe the weight averaging process, discuss the influence of neighbor selection and averaging frequency, and mention weighted averaging variations.
+\item \textbf{NN-Consensus:} Explain the selection of the best-performing network and its potential benefits and drawbacks.
+\item \textbf{Experience Sharing:} Detail how agents share experiences, discuss asynchronous vs. synchronous sharing, and highlight its advantages in sparse interaction environments.
+\end{itemize}
+\end{itemize}
+
+\section{Experimental Setup}
+\begin{itemize}
+\item Introduce the custom "collect the items" multi-agent environment:
+\begin{itemize}
+\item Describe the environment's dynamics, agent goals, and challenges.
+\item Specify the action space (continuous and discrete) and observation space design.
+\item Explain the reward structure, emphasizing the components that encourage cooperation.
+\end{itemize}
+\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
+\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
+\item Define the evaluation metrics: average episode length and average reward.
+\end{itemize}
+
+\section{Results and Evaluation}
+\begin{itemize}
+\item \textbf{Performance comparison:}
+\begin{itemize}
+\item Present the results of each distributed strategy against the centralized training baseline.
+\item Use graphs and statistical analysis to compare the average episode length and average reward.
+\item Highlight which neighbor-based methods perform comparably to centralized training.
+\end{itemize}
+\item \textbf{Scalability analysis:}
+\begin{itemize}
+\item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
+\item Show how each method scales with the increasing complexity, using appropriate visualizations.
+\item Discuss the implications of using pre-trained models with a larger number of agents.
+\end{itemize}
+\item \textbf{Communication overhead analysis:}
+\begin{itemize}
+\item Quantify the amount of information exchange for each strategy.
+\item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
+\item Discuss the trade-offs between performance and communication efficiency.
+\item Mention potential techniques for reducing communication overhead.
+\end{itemize}
+\end{itemize}
+
+\section{Conclusion}
+\begin{itemize}
+\item Summarize the key findings of the paper.
+\item Emphasize the viability of neighbor-based methods as alternatives to centralized training in MARL.
+\item Discuss the trade-offs observed in terms of performance, scalability, and communication overhead.
+\item Suggest potential directions for future research, such as exploring hybrid approaches or more advanced communication protocols.
+\end{itemize}
 

### 2024-09-17 paper-2024-sac-marl-neighbouring-strategies.tex
chore: on paper
chore: add details

@@
 
-\author{Ben Trovato}
-\authornote{Dr.~Trovato insisted his name be first.}
+\author{Nicolò Malucelli}
 \orcid{1234-5678-9012}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin} 
-  \state{Ohio} 
-  \country{USA}
-  \postcode{43017-6221}  
+  \institution{University of Bologna}
+  \streetaddress{Via dell'Università, 50}
+  \city{Cesena} 
+  \country{Italy}
 }
-\email{trovato@corporation.com}
+\email{nicolò.malucelli@studio.unibo.it}
 
-\author{G.K.M. Tobin}
-\authornote{The secretary disavows any knowledge of this author's actions.}
+\author{Davide Domini}
+\orcid{1234-5678-9012}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin} 
-  \state{Ohio} 
-  \country{USA}
-  \postcode{43017-6221}  
+  \institution{University of Bologna}
+  \streetaddress{Via dell'Università, 50}
+  \city{Cesena} 
+  \country{Italy}
 }
-\email{webmaster@marysville-ohio.com}
+\email{davide.domini@unibo.it}
 
-\author{Lars Th{\o}rv{\"a}ld}
-\authornote{This author is the
-  one who did all the really hard work.}
+\author{Gianluca Aguzzi}
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla} 
-  \country{Iceland}}
-\email{larst@affiliation.org}
+  \institution{University of Bologna}
+  \streetaddress{Via dell'Università, 50}
+  \city{Cesena} 
+  \country{Italy}
+}
+\email{gianluca.aguzzi@unibo.it}
 
-\author{Valerie B\'eranger}
+\author{Mirko Viroli}
 \affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
+  \institution{University of Bologna}
+  \streetaddress{Via dell'Università, 50}
+  \city{Cesena} 
+  \country{Italy}
 }
-\author{Aparna Patel} 
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh} 
- \state{Arunachal Pradesh}
- \country{India}}
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu} 
-  \state{Beijing Shi}
-  \country{China}
-}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas} 
-  \country{USA}
-  \postcode{78229}}  
-\email{cpalmer@prl.com}
+\email{mirko.viroli@unibo.it}
 
 % The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{B. Trovato et al.}
+\renewcommand{\shortauthors}{N. Malucelli et al.}
 
@@
 \end{abstract}
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
 %
@@
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{Multi-Agent Reinforcement Learning, Decentralized Training, Neighbor-Based Methods, Scalability, Communication Efficiency}
 \maketitle
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-bibliography}
+\bibliography{bibliography}
 

### 2024-09-29 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add concept
chore: fix the compile error
anonymized paper
rephrase abstract

@@
 
-\author{Nicolò Malucelli}
+% \author{Nicolò Malucelli}
+% \orcid{1234-5678-9012}
+% \affiliation{%
+%   \institution{University of Bologna}
+%   \streetaddress{Via dell'Università, 50}
+%   \city{Cesena} 
+%   \country{Italy}
+% }
+% \email{nicolo.malucelli@studio.unibo.it}
+
+% \author{Davide Domini}
+% \orcid{1234-5678-9012}
+% \affiliation{%
+%   \institution{University of Bologna}
+%   \streetaddress{Via dell'Università, 50}
+%   \city{Cesena} 
+%   \country{Italy}
+% }
+% \email{davide.domini@unibo.it}
+
+% \author{Gianluca Aguzzi}
+% \affiliation{%
+%   \institution{University of Bologna}
+%   \streetaddress{Via dell'Università, 50}
+%   \city{Cesena} 
+%   \country{Italy}
+% }
+% \email{gianluca.aguzzi@unibo.it}
+
+% \author{Mirko Viroli}
+% \affiliation{%
+%   \institution{University of Bologna}
+%   \streetaddress{Via dell'Università, 50}
+%   \city{Cesena} 
+%   \country{Italy}
+% }
+% \email{mirko.viroli@unibo.it}
+
+% % The default list of authors is too long for headers}
+% \renewcommand{\shortauthors}{N. Malucelli et al.}
+
+\author{Anonymous Author}
 \orcid{1234-5678-9012}
 \affiliation{%
-  \institution{University of Bologna}
-  \streetaddress{Via dell'Università, 50}
-  \city{Cesena} 
-  \country{Italy}
+  \institution{Anonymous university}
+  \country{Anonymous location}
 }
-\email{nicolò.malucelli@studio.unibo.it}
-
-\author{Davide Domini}
-\orcid{1234-5678-9012}
-\affiliation{%
-  \institution{University of Bologna}
-  \streetaddress{Via dell'Università, 50}
-  \city{Cesena} 
-  \country{Italy}
-}
-\email{davide.domini@unibo.it}
-
-\author{Gianluca Aguzzi}
-\affiliation{%
-  \institution{University of Bologna}
-  \streetaddress{Via dell'Università, 50}
-  \city{Cesena} 
-  \country{Italy}
-}
-\email{gianluca.aguzzi@unibo.it}
-
-\author{Mirko Viroli}
-\affiliation{%
-  \institution{University of Bologna}
-  \streetaddress{Via dell'Università, 50}
-  \city{Cesena} 
-  \country{Italy}
-}
-\email{mirko.viroli@unibo.it}
-
-% The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{N. Malucelli et al.}
+% \email{anonymous.author@studio.unibo.it}
+\renewcommand{\shortauthors}{A. Author et al.}
 
 \begin{abstract}
-  Multi-Agent Reinforcement Learning (MARL) is gaining popularity as a powerful framework for training agents to collaborate and compete in complex environments.
-However, MARL introduces unique challenges, such as non-stationarity and partial observability, that complicate the training process.
-  While centralized training methods can address some of these challenges, they often face scalability limitations as the number of agents grows.
-This paper investigates the effectiveness of various neighbor-based decentralized training strategies as a viable alternative to centralized training.
-We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods in a custom multi-agent environment and compare their performance against centralized training.
-Our results show that neighbor-based methods can achieve comparable performance to centralized training while offering improved scalability and communication efficiency.
-  We discuss the trade-offs between these methods and provide insights into their applicability in different scenarios.
-  %% More -- add the fact that this make it possible to train agents in a decentralized manner, which is more realistic and scalable than centralized training.
+Multi-Agent Reinforcement Learning  is gaining popularity as a powerful extension of
+  Single-Agent Reinforcement Learning for training collaborative or competitive agents
+  in complex environments. 
+%
+MARL introduces unique challenges, such as non-stationarity, partial observability, 
+  and credit assignment that complicate the learning process.  
+%
+Typically, in the literature, centralized training methods are used to tackle some of these challenges, 
+  although they often face scalability limitations as the number of agents grows.
+%
+For this reason, decentralized training techniques have been proposed, however, 
+  generally they have a longer convergence time compared to centralized ones 
+  and may lead to instability.
+%
+This paper investigates the effectiveness of various neighbor-based decentralized training strategies 
+  as a viable alternative to centralized training. 
+%  
+We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods 
+  in a custom multi-agent environment and compare their performance against centralized training. 
+%  
+Our results show that neighbor-based methods can achieve comparable performance to centralized training 
+  while offering improved scalability and communication efficiency. 
+%
+% Finally, we discuss the trade-offs between these methods and provide insights into their applicability 
+%   in different scenarios.
 \end{abstract}
+
 %
@@
 \end{itemize}
-
 \section{Experimental Setup}
@@
 \bibliography{bibliography} 
+\nocite{*}
 

### 2024-09-30 paper-2024-sac-marl-neighbouring-strategies.tex
add todonotes style

@@
 \usepackage{booktabs} % For formal tables
+\usepackage{mytodonotes}
 
@@
 \section{Introduction}
-\begin{itemize}
-\item Highlight the growing importance of MARL and its applications.
-\item Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
-\item Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
-\item Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
-\item State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
-\end{itemize}
+
+\gianlu{
+Highlight the growing importance of MARL and its applications.
+
+Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
+
+Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
+
+Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
+
+State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
+}
 

### 2024-09-30 paper-2024-sac-marl-neighbouring-strategies.tex
init intro

@@
 
+In recent years, machine learning and deep learning methods have gained more and more interests. 
+%
+In particular, regarding Multi-Agents Systems and Robotics, \emph{Reinforcement Learning} showed promising results.
+
+Single-Agent Reinforcement Learning (SARL) has been extensively studied and used in literature to solve tasks in a broad range 
+  of applied scenarios~\cite{DBLP:journals/air/SinghKS22,DBLP:journals/artmed/CoronatoNPP20,DBLP:journals/comsur/LuongHGNWLK19}.
+
 \section{Background}
@@
 \bibliography{bibliography}
-\nocite{*}
 

### 2024-10-01 paper-2024-sac-marl-neighbouring-strategies.tex
chore: draft introduction (need citations)

--- 2024-09-30 paper-2024-sac-marl-neighbouring-strategies.tex
@@
 \begin{abstract}
-Multi-Agent Reinforcement Learning  is gaining popularity as a powerful extension of
-  Single-Agent Reinforcement Learning for training collaborative or competitive agents
+Multi-agent reinforcement learning  is gaining popularity as a powerful extension of
+  single-agent reinforcement learning for training collaborative or competitive agents
   in complex environments. 
@@
 
-\gianlu{
-Highlight the growing importance of MARL and its applications.
+Distributed artificial intelligence has emerged as a prominent research area in recent years, 
+evolving from its roots in multi-agent systems engineering 
+through advancements in distributed learning. 
+%
+This evolution has encompassed collective behavior learning (e.g., COIN) 
+and culminated in the modern field of multi-agent deep reinforcement learning (MADRL). 
+%
+MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
+ranging from cooperative to competitive, 
+as demonstrated in various case studies involving video games, swarm robotics, 
+and traffic management. 
+%
+This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
+a particularly active and impactful area of research within MADRL.
 
-Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
+Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
+ (e.g., COMA, MAPPO, MADPG), 
+ where a centralized learner trains distributed policies that are subsequently executed independently. 
+ While facilitating decentralized runtime operation and avoiding single points of failure, 
+ this approach typically entails an offline learning phase (using simulators and centralized computation) 
+ followed by online execution with no further learning. 
+ This inherent limitation hinders adaptation to changing environments or tasks at runtime.  
+ While fully independent learners offer a potential solution for online learning,
+ they often underperform centralized counterparts due to instability in training and a lack of differentiation between agents and their interactions with the environment. 
+ %
+ However, in many real-world multi-agent systems, 
+ agents only interact with a limited subset of the overall system, 
+ as exemplified by limited sensing ranges in swarm robotics or localized interactions.  
+ This observation also holds true in other natural systems, such as animal herds.
 
-Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
+Therefore, 
+this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information. 
+This approach aims to: 
+\begin{itemize}
+  \item incorporate richer information compared to independent learners, and
+  \item facilitate the emergence of collective behaviors through local interactions.
+\end{itemize}
+Specifically, we investigate three distinct neighboring-based training strategy encompassing both neural network-based approaches 
+(e.g., neighboring averaging and consensus) 
+and experience-based methods inspired by centralized experience sharing. 
+We demonstrate the effectiveness of these strategies in comparison to both centralized and fully distributed approaches, 
+highlighting how neighborhood-based policies offer a compelling compromise between these two extremes.
 
-Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
+The remainder of this paper is structured as follows.
+Section~\ref{sec:background} provides an overview of multi-agent reinforcement learning,
+highlighting the key challenges and training paradigms.
+Section~\ref{sec:neighboring} introduces the proposed neighboring-based training strategies,
+detailing their implementation and operation.
+Section~\ref{sec:experiments} presents the experimental setup and evaluation metrics.
+Section~\ref{sec:results} discusses the results of the experiments,
+comparing the performance of the neighboring-based methods against centralized training.
+Finally, Section~\ref{sec:conclusion} concludes the paper,
+summarizing the key findings and outlining potential future research directions.
 
-State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
-}
-
-\section{Background}
+\section{Background}\label{sec:background}
 \begin{itemize}
@@
 
-\section{Neighboring-Based Distributed Learning Strategies}
+\section{Neighboring-Based Distributed Learning Strategies}\label{sec:neighboring}
 \begin{itemize}
@@
 \end{itemize}
-\section{Experimental Setup}
+\section{Experimental Setup}\label{sec:experiments}
 \begin{itemize}
@@
 
-\section{Results and Evaluation}
+\section{Results and Evaluation}\label{sec:results}
 \begin{itemize}
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 \begin{itemize}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: on formalization

@@
 \begin{abstract}
-Multi-agent reinforcement learning  is gaining popularity as a powerful extension of
+Multi-agent deep reinforcement learning (MADRL) is gaining popularity as a powerful extension of
   single-agent reinforcement learning for training collaborative or competitive agents
@@
 %
-MARL introduces unique challenges, such as non-stationarity, partial observability, 
+MADRL, however, introduces unique challenges, such as non-stationarity, partial observability, 
   and credit assignment that complicate the learning process.
@@
 %
-This paper investigates the effectiveness of various neighbor-based decentralized training strategies 
+This paper investigates the effectiveness of various neighbor-based decentralized training strategies based on the well-known deep-q learning algorithm 
   as a viable alternative to centralized training. 
 %  
-We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods 
+We evaluate experience sharing, nearest neighboring averaging, and nearest neighboring consensus methods 
   in a custom multi-agent environment and compare their performance against centralized training. 
@@
   <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
+  <concept_significance>300</concept_sigagentnificance>
  </concept>
@@
 Therefore, 
-this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information. 
+this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information---in this research area is typically referred to as \emph{networked agents}.
 This approach aims to: 
@@
 
-\section{Background}\label{sec:background}
+\section{Background and Motivation}\label{sec:background}
+Multi-agent reinforcement learning is an extension of a sequientail decision-making process, 
+where multiple agents interact with each other and the environment.
+In particular, each agent in the system aims to maximize its own reward,
+which is typically a function of the global state (sometime not known, aka partial observable) and the joint action taken by all agents.
+%
+In doing that, each agent perceive the environment through its own observation function,
+which maps the global state to the agent's local observation and perform an action based on its policy.
+%
+This action is then combined with the actions of other agents to form a joint action,
+which is used to update the global state and reward.
+
+MADRL is a subfield of reinforcement learning that focuses on training multiple agents to interact with each other within a shared environment.
+%
+In this \emph{deep} variant, agents are typically represented by neural networks that learn to maximize a shared (or individual) reward signal.
+% 
+%
+MADRL is a wide area, and it encompassed a variety of scenarios, 
+such as cooperative (e.g., multi-agent pathfinding), 
+competitive (e.g., multi-agent games), 
+and mixed environments.
+%
+In this paper, we focus on cooperative scenarios, where agents must collaborate to achieve a common goal,
+introducing a common formalization (networked agents) and discussing the key concepts of joint action space, shared reward, partial observability, and credit assignment, following by different training schemes (centralized and distributed), with a discussion on the state of the art and motivation for our work.
+\subsection{Formalization}
+Since MARL is a broad field, it is essential to provide a formalization to guide the discussion.
+In this paper, we consider a partially observable networked multi-agent system (PONMAS) as a tuple $(\mathcal{G}, \mathcal{S}, \mathcal{A}, \mathcal{O}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
+$\mathcal{G} = (N, E)$ is a communication graph, where $N = {1, \dots, n}$ is the set of $n$ agents and $E \subseteq N \times N$ represents the communication links between agents.
+Time-varying graphs $\mathcal{G}_t = (N, E_t)$ can be used to represent communication evolving over time $t$.
+%
+$\mathcal{S}$ is the global state space.
+%
+$\mathcal{A} = \mathcal{A}^1 \times \dots \times \mathcal{A}^n$ is the joint action space, where $\mathcal{A}^i$ is the action space of agent $i$.
+%
+$\mathcal{O} = \mathcal{O}^1 \times \dots \times \mathcal{O}^n$ is the joint observation space, where $\mathcal{O}^i$ is the observation space for agent $i$. 
+%
+Observations $o^i \in \mathcal{O}^i$ provide partial information about the global state.
+$\mathcal{P}: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \to [0, 1]$ is the state transition function, describing the probability of transitioning to a new state $s' \in \mathcal{S}$ given the current state $s \in \mathcal{S}$ and joint action $a \in \mathcal{A}$.
+%
+$\mathcal{R} = {\mathcal{R}^i}_{i \in N}$, where $\mathcal{R}^i: \mathcal{S} \times \mathcal{A} \to \mathbb{R}$ is the reward function for agent $i$.
+%
+$\gamma \in [0, 1]$ is the discount factor.
+%
+Each agent $i$ at time $t$ receives an observation $o^i_t \in \mathcal{O}^i$, takes an action $a^i_t \in \mathcal{A}^i$ based on its local policy $\pi^i: \mathcal{O}^i \times \mathcal{A}^i \to [0,1]$, and receives a reward $r^i_{t+1} = \mathcal{R}^i(s_t, a_t)$.
+%
+The global state evolves according to $\mathcal{P}$. 
+Agents can exchange information with their neighbors in $\mathcal{G}$ (or $\mathcal{G}t$ if the graph is time-varying). 
+%
+The objective is typically to maximize the expected discounted sum of rewards $\sum{t=0}^{\infty} \gamma^t r^i_t$ for each agent $i$, 
+or some global reward function like the average reward over all agents.
+Formally, it can be defined as:
+\[ J(\{\pi^i\}) = \lim_{T \to \infty} \mathbb{E} \left[ \frac{1}{T} \sum_{t=0}^{T-1} \frac{1}{N} \sum_{i \in \mathcal{N}} R^i(s_t, a_t) \right] \]
+
+In doing this, agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function or Q-value. 
+The latter represents the expected cumulative discounted reward the agent will receive by taking action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and then following its policy $\pi^i$:
+
+\[ Q^i(s, a) = \mathbb{E}_{\pi^i} \left[ \sum_{t=0}^{\infty} \gamma^t r^i_{t+1} | s_0 = s, a_0 = a \right] \]
+
+Similar to the individual reward function, a global average reward function can be defined as $\bar{\mathcal{R}}(s, a) = \frac{1}{n} \sum_{i=1}^n \mathcal{R}^i(s,a)$, leading to a global average Q-value:
+
+\[ \bar{Q}(s, a) = \mathbb{E}_{\pi} \left[ \sum_{t=0}^{\infty} \gamma^t \bar{\mathcal{R}}(s_t, a_t) | s_0 = s, a_0 = a \right] \]
+
+where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy.  The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
+%\subsection{Key Concepts}
+
+\subsection{Training Schemes}
+
+\subsection{State of the Art}
+
+\subsection{Motivation}
+
 \begin{itemize}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
on training schema

@@
 
-\subsection{Training Schemes}
+\subsection{Learning Schemes}
+Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
+Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE).
 
+\paragraph{Centralized Training with Decentralized Execution (CTDE)}
+In CTDE, a central learner trains all agents, 
+but execution of the learned policy is decentralized. 
+This process typically involves two phases:
+\begin{itemize}
+    \item \textbf{Offline training:} agents interact with a simulator or environment, 
+    gathering experience data used to update the central learner's policy.
+    \item \textbf{Online execution:} agents deploy the learned policy in the environment without further learning.
+\end{itemize}
+This approach offers several benefits.  
+Leveraging a centralized dataset allows for efficient learning, 
+potentially exploiting global information, 
+which is crucial in cooperative scenarios requiring coordinated actions. 
+Furthermore, decentralized execution allows agents to act independently after training.
+%
+However, CTDE has limitations. 
+Scalability can become problematic with a large number of agents. 
+The reliance on a central learner hinders adaptation to dynamic environments or tasks during runtime.
+\sloppy
+\paragraph{Decentralized Training with Decentralized Execution (DTDE)}
+DTDE eliminates the central learner; each agent learns independently. 
+Inter-agent cooperation and communication can be incorporated during both training and execution. 
+Unlike CTDE, training and execution phases are not necessarily separate. 
+Simultaneous learning and execution allow for adaptation to changing environments or tasks at runtime.
+%
+Key advantages of DTDE include scalability with the number of agents and adaptability to dynamic environments.
+%
+However, DTDE faces challenges. 
+Convergence time is often longer compared to centralized training. 
+The lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions. 
+Online learning in DTDE can introduce non-stationarity if agents do not account for other agents' evolving policies during training, 
+as the environment effectively changes from each agent's perspective.
 \subsection{State of the Art}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
on sota (need to be filled)

@@
 \subsection{State of the Art}
+Multi-agent reinforcement learning is a longstanding research area with a rich literature, starting 
+from seminal works like [cite ] and [cite] to more recent contributions like [cite] and [cite].
+%
+In the following, we briefly discuss some of the most relevant approaches in the field.
+\paragraph{Independent Learners}
+
+\paragraph{Centralized Actor-Critic Methods}
 
 \subsection{Motivation}
-
-\begin{itemize}
-\item Introduce Multi-Agent Reinforcement Learning (MARL) and its specific challenges.
-\item Provide a formalization (networked agents?) and explain the key concepts: joint action space, shared reward, partial observability, and credit assignment.
-\item Explain different MARL training schemes: centralized training (CTCE, CTDE), distributed training (DTDE).
-\end{itemize}
 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
draft q-leaerning (think where should we place it)

@@
 \usepackage{booktabs} % For formal tables
+\usepackage{graphicx}
+\usepackage{autobreak}
 \usepackage{mytodonotes}
@@
 
-where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy.  The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
+where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy. 
+The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
+There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep q-learning algorithm.
+\subsubsection{Deep Q-Learning Formalization}
+deep q-learning utilizes a deep neural network, 
+often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
+This network takes the state $s$ as input and outputs a vector of Q-values, one for each possible action $a \in \mathcal{A}$.  
+The optimal action-value function, denoted $Q^*(s, a)$, satisfies the Bellman optimality equation:
+
+\[ Q^*(s, a) = \mathbb{E}_{s' \sim \mathcal{P}} \left[ r + \gamma \max_{a'} Q^*(s', a') | s, a \right] \]
+
+where $\mathcal{P}$ is the state transition probability distribution.  
+Deep Q-learning aims to train the Q-network to approximate $Q^*(s, a)$ by minimizing the loss function:
+
+\[ \mathcal{L}(\theta) = \mathbb{E}_{(s, a, r, s') \sim \mathcal{D}} \left[ \left( r + \gamma \max_{a'} Q(s', a'; \theta^-) - Q(s, a; \theta) \right)^2 \right] \]
+
+where $\theta$ are the parameters of the Q-network, $\theta^-$ are the parameters of a target Q-network (used for stability), 
+and $\mathcal{D}$ is the experience replay buffer, a collection of past experiences $(s, a, r, s')$.
+%
+In the multi-agent setting, each agent $i$ has its own Q-network $Q^i(o^i, a^i; \theta^i)$ that takes its local observation $o^i$ as input.  
+For centralized training, the global state $s$ can be used as input. 
+The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., independent Q-learning, value decomposition methods).  
+For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:
+\begin{equation}
+  \resizebox{\linewidth}{!}{$
+  \mathcal{L}^i(\theta^i) = \mathbb{E}_{(o^i, a^i, r^i, o'^i) \sim \mathcal{D}^i} \left[ \left( r^i + \gamma \max_{a'^i} Q^i(o'^i, a'^i; \theta^{i-}) - Q^i(o^i, a^i; \theta^i) \right)^2 \right]
+  $}
+  \end{equation}
 %\subsection{Key Concepts}
@@
 
+\paragraph{Neighboring-Based Methods}
 \paragraph{Centralized Actor-Critic Methods}
@@
 \subsection{Motivation}
-
+MADRL faces a critical challenge in balancing scalability and performance.  
+Centralized training methods, while effective, often suffer from computational bottlenecks and difficulties scaling to large numbers of agents. 
+While distributed training approaches offer improved scalability, 
+they frequently assume independent learners, 
+neglecting crucial inter-agent coordination and leading to suboptimal global performance.  
+%
+Neighbor-based methods have shown promise in simpler, tabular settings by enabling localized coordination,
+but their integration with deep reinforcement learning remains largely unexplored. 
+This work bridges this gap by introducing a novel approach that combines the power of deep learning with the scalability of neighbor-based communication.  
+Our method aims to achieve both efficient decentralized learning and effective coordination, enabling online adaptation and robust performance in complex multi-agent environments.
 \section{Neighboring-Based Distributed Learning Strategies}\label{sec:neighboring}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
drafting the k-nearest neighbor averaging

@@
 \section{Neighboring-Based Distributed Learning Strategies}\label{sec:neighboring}
+This section introduces three neighboring-based distributed learning strategies for multi-agent reinforcement learning. 
+These strategies leverage local interactions between agents to improve learning efficiency and coordination.
+For this investigation, we focus on deep Q-learning as the underlying learning algorithm,
+and we consider the following strategies:
+ k-nearest neighbor averaging, k-nearest neighbor consensus, and experience sharing.
+
+Since these strategies are in general based on the notion of k-nearest neighbors,
+we first introduce this concept and then describe each strategy in detail.
+Formally, consider a \emph{weighted} communication graph $\mathcal{G} = (N, E, W)$, where $N$ is the set of agents, where $W: E \rightarrow \mathbb{R}^+$ is a weight function assigning a positive weight to each edge.
+Let $d(i,j)$ denote the shortest path length between agents $i$ and $j$ in the weighted graph $\mathcal{G}$. 
+This can be calculated, for instance, using Dijkstra's algorithm. 
+The length of a path is the sum of the weights of the edges along the path. If no path exists between $i$ and $j$, we set $d(i,j) = \infty$.
+%
+Then, the set of $k$-nearest neighbors of agent $i$ is defined as:
+$$ \mathcal{N}_k(i) = { j \in N \setminus {i} \mid \text{rank}(d(i,j)) \leq k } $$
+where $\text{rank}(d(i,j))$ denotes the rank of the distance $d(i,j)$ among all distances from agent $i$ to other agents in $N \setminus {i}$, sorted in ascending order (e..g, $\text{rank}(d(i,j)) = 1$ for the smallest distance).
+Ties can be broken arbitrarily.
+
+\subsection{K-Nearest Neighbor Averaging}
+This approach averages an agent's Q-values with those of its nearest neighbors. 
+Each agent maintains a local Q-network and shares its Q-values with its neighbors. 
+The neighbors average the received Q-values and use the result to update their own Q-networks. 
+This leverages the collective knowledge of neighboring agents to improve learning.
+%
+Formally, giving $\theta^t_i, i \in N$ the parameters of the Q-networks of the agent $i$ at the time $t$,
+the update rule for agent $i$ at time $t+1$ is:
+\begin{equation}
+  \theta^{t+1}_i = \theta^t_i + \alpha \sum_{j \in \mathcal{N}_k(i)} \frac{1}{k} \theta^t_j
+\end{equation}
+
+\subsection{Nearest Neighboring Consensus}
+
+\subsection{Experience Sharing}
+
 \begin{itemize}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
reduce the domain

@@
 \section{Introduction}
-
-Distributed artificial intelligence has emerged as a prominent research area in recent years, 
-evolving from its roots in multi-agent systems engineering 
-through advancements in distributed learning. 
+The increasing complexity of real-world systems, from robotic swarms to smart grids, demands intelligent control strategies capable of adapting to dynamic and often unpredictable environments.
+In this direction, reinforcement learning (RL) has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
 %
-This evolution has encompassed collective behavior learning (e.g., COIN) 
-and culminated in the modern field of multi-agent deep reinforcement learning (MADRL). 
+Moving beyond single-agent settings, multi-agent reinforcement learning (MARL) extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
+%
+Recent advances in deep learning have further revolutionized the field, enabling the training of complex policies in high-dimensional state and action spaces, leading to the emergence of multi-agent deep reinforcement learning (MADRL).
 %
@@
 ranging from cooperative to competitive, 
-as demonstrated in various case studies involving video games, swarm robotics, 
+as demonstrated in various case studies involving video games, robotics,
 and traffic management. 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: starting adding references

--- 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
@@
 \section{Introduction}
-
-Distributed artificial intelligence has emerged as a prominent research area in recent years, 
-evolving from its roots in multi-agent systems engineering 
-through advancements in distributed learning. 
+The increasing complexity of real-world systems, from robotic swarms to smart grids, demands intelligent control strategies capable of adapting to dynamic and often unpredictable environments.
 %
-This evolution has encompassed collective behavior learning (e.g., COIN) 
-and culminated in the modern field of multi-agent deep reinforcement learning (MADRL). 
+In this direction, reinforcement learning (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
+%
+Moving beyond single-agent settings, multi-agent reinforcement learning (MARL)~\cite{bucsoniu2010multi} extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
+%
+Recent advances in deep learning have further revolutionized the field, 
+enabling the training of complex policies in high-dimensional state and action spaces, 
+leading to the emergence of multi-agent deep reinforcement learning (MADRL)~\cite{gronauer2022multi}.
 %
 MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
-ranging from cooperative to competitive, 
-as demonstrated in various case studies involving video games, swarm robotics, 
+ranging from cooperative~\cite{gupta2017cooperative} to competitive~\cite{tampuu2017multiagent}, 
+as demonstrated in various case studies involving video games~\cite{shao2019survey}, robotics~\cite{orr2023multi},
 and traffic management. 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
start to put citations

@@
 This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
-a particularly active and impactful area of research within MADRL.
+a particularly active and impactful area of research within MADRL~\cite{oroojlooy2023review}.
 
+\sloppy
 Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
- (e.g., COMA, MAPPO, MADPG), 
+ (e.g., COMA~\cite{foerster2018counterfactual}, MAPPO~\cite{yu2022surprising}, MADPG), 
  where a centralized learner trains distributed policies that are subsequently executed independently. 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: minor on aestetics

--- 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
@@
 %
-In this direction, reinforcement learning (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
+In this direction, \emph{reinforcement learning} (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
 %
-Moving beyond single-agent settings, multi-agent reinforcement learning (MARL)~\cite{bucsoniu2010multi} extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
+Moving beyond single-agent settings, \emph{multi-agent reinforcement learning} (MARL)~\cite{bucsoniu2010multi} extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
 %
@@
 enabling the training of complex policies in high-dimensional state and action spaces, 
-leading to the emergence of multi-agent deep reinforcement learning (MADRL)~\cite{gronauer2022multi}.
+leading to the emergence of \emph{multi-agent deep reinforcement learning} (MADRL)~\cite{gronauer2022multi}.
 %
@@
 %
-This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
-a particularly active and impactful area of research within MADRL.
+This paper focuses on the subdomain of \emph{cooperative multi-agent reinforcement learning}, 
+a particularly active and impactful area of research within MADRL~\cite{oroojlooy2023review}.
 
+\sloppy
 Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
- (e.g., COMA, MAPPO, MADPG), 
+ (e.g., COMA~\cite{foerster2018counterfactual}, MAPPO~\cite{yu2022surprising}, MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17}, QMIX~\cite{DBLP:conf/icml/RashidSWFFW18}, QTRAN~\cite{DBLP:conf/icml/SonKKHY19}),
  where a centralized learner trains distributed policies that are subsequently executed independently. 
@@
  This inherent limitation hinders adaptation to changing environments or tasks at runtime.  
- While fully independent learners offer a potential solution for online learning,
+% 
+While fully independent learners~\cite{abed2016comparison} offer a potential solution for online learning,
  they often underperform centralized counterparts due to instability in training and a lack of differentiation between agents and their interactions with the environment. 
@@
 However, in many real-world multi-agent systems, 
- agents only interact with a limited subset of the overall system, 
+ agents only interact with a limited subset of the overall system (also called \emph{networked agents}),
  as exemplified by limited sensing ranges in swarm robotics or localized interactions.  
  This observation also holds true in other natural systems, such as animal herds.
-
+%
 Therefore, 
-this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information---in this research area is typically referred to as \emph{networked agents}.
+this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information.
 This approach aims to: 
-\begin{itemize}
-  \item incorporate richer information compared to independent learners, and
-  \item facilitate the emergence of collective behaviors through local interactions.
-\end{itemize}
-Specifically, we investigate three distinct neighboring-based training strategy encompassing both neural network-based approaches 
+i) incorporate richer information compared to independent learners, and
+ii) facilitate the emergence of collective behaviors through local interactions between networked agents.
+Specifically, we investigate three distinct neighboring-based training strategies encompassing both neural network-based approaches 
 (e.g., neighboring averaging and consensus) 
-and experience-based methods inspired by centralized experience sharing. 
+and experience-based methods inspired by centralized experience sharing~\cite{DBLP:conf/nips/ChristianosSA20}. 
 We demonstrate the effectiveness of these strategies in comparison to both centralized and fully distributed approaches, 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: continue in refine main concepts

@@
 \section{Background and Motivation}\label{sec:background}
-Multi-agent reinforcement learning is an extension of a sequientail decision-making process, 
-where multiple agents interact with each other and the environment.
-In particular, each agent in the system aims to maximize its own reward,
-which is typically a function of the global state (sometime not known, aka partial observable) and the joint action taken by all agents.
+MARL is an extension of a sequential decision-making process, 
+where multiple \emph{agents} interact with each other and a shared \emph{environment}.
+In particular, each agent in the system aims to maximize its own \emph{reward signal} (i.e., a scalar feedback signal),
+which is typically a function of the global state (sometime not known, making the system \emph{partial observable}) and the joint action taken by all agents.
 %
-In doing that, each agent perceive the environment through its own observation function,
-which maps the global state to the agent's local observation and perform an action based on its policy.
+In doing that, each agent perceive the environment through its own \emph{observation function},
+which maps the global state to the agent's local observation and perform an action based on its \emph{policy} (i.e., a mapping from observations to actions).
 %
-This action is then combined with the actions of other agents to form a joint action,
+This chosen action is then combined with the actions of other agents forming a \emph{joint action},
 which is used to update the global state and reward.
 
-MADRL is a subfield of reinforcement learning that focuses on training multiple agents to interact with each other within a shared environment.
-%
-In this \emph{deep} variant, agents are typically represented by neural networks that learn to maximize a shared (or individual) reward signal.
-% 
-%
-MADRL is a wide area, and it encompassed a variety of scenarios, 
-such as cooperative (e.g., multi-agent pathfinding), 
-competitive (e.g., multi-agent games), 
-and mixed environments.
-%
-In this paper, we focus on cooperative scenarios, where agents must collaborate to achieve a common goal,
-introducing a common formalization (networked agents) and discussing the key concepts of joint action space, shared reward, partial observability, and credit assignment, following by different training schemes (centralized and distributed), with a discussion on the state of the art and motivation for our work.
+In this paper, we focus on cooperative MADRL scenarios (so the deep version of MARL), 
+where agents must collaborate to achieve a common goal.
+In the following, we provide an overview of the key concepts in MADRL, 
+including the formalization of the problem, the deep Q-learning algorithm, and the training paradigms used in the literature.
 \subsection{Formalization}
-Since MARL is a broad field, it is essential to provide a formalization to guide the discussion.
-In this paper, we consider a partially observable networked multi-agent system (PONMAS) as a tuple $(\mathcal{G}, \mathcal{S}, \mathcal{A}, \mathcal{O}, \mathcal{P}, \mathcal{R}, \gamma)$, where:
-$\mathcal{G} = (N, E)$ is a communication graph, where $N = {1, \dots, n}$ is the set of $n$ agents and $E \subseteq N \times N$ represents the communication links between agents.
+Since MADRL is a broad field, it is essential to provide a formalization to guide the discussion.
+In this paper, we consider partially observable networked markov decision process (PONMDP)~\cite{DBLP:journals/tac/AdlakhaLG12} as a tuple $(\mathcal{G}, \mathcal{S}, \mathcal{A}, \mathcal{O}, \mathcal{P}, \mathcal{R}, \gamma)$, where
+
+\begin{itemize}
+  \item $\mathcal{G} = (N, E)$ is a communication graph, where $N$ is the set of $n$ agents and $E \subseteq N \times N$ represents the communication links between agents.
 Time-varying graphs $\mathcal{G}_t = (N, E_t)$ can be used to represent communication evolving over time $t$.
-%
-$\mathcal{S}$ is the global state space.
-%
-$\mathcal{A} = \mathcal{A}^1 \times \dots \times \mathcal{A}^n$ is the joint action space, where $\mathcal{A}^i$ is the action space of agent $i$.
-%
-$\mathcal{O} = \mathcal{O}^1 \times \dots \times \mathcal{O}^n$ is the joint observation space, where $\mathcal{O}^i$ is the observation space for agent $i$. 
-%
-Observations $o^i \in \mathcal{O}^i$ provide partial information about the global state.
-$\mathcal{P}: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \to [0, 1]$ is the state transition function, describing the probability of transitioning to a new state $s' \in \mathcal{S}$ given the current state $s \in \mathcal{S}$ and joint action $a \in \mathcal{A}$.
-%
-$\mathcal{R} = {\mathcal{R}^i}_{i \in N}$, where $\mathcal{R}^i: \mathcal{S} \times \mathcal{A} \to \mathbb{R}$ is the reward function for agent $i$.
-%
-$\gamma \in [0, 1]$ is the discount factor.
-%
-Each agent $i$ at time $t$ receives an observation $o^i_t \in \mathcal{O}^i$, takes an action $a^i_t \in \mathcal{A}^i$ based on its local policy $\pi^i: \mathcal{O}^i \times \mathcal{A}^i \to [0,1]$, and receives a reward $r^i_{t+1} = \mathcal{R}^i(s_t, a_t)$.
+  \item $\mathcal{S}$ is the global state space.
+  \item $\mathcal{A} = \mathcal{A}^1 \times \dots \times \mathcal{A}^n$ is the joint action space, where $\mathcal{A}^i$ is the action space of agent $i$.
+  \item $\mathcal{O} = \mathcal{O}^1 \times \dots \times \mathcal{O}^n$ is the joint observation space, where $\mathcal{O}^i$ is the observation space for agent $i$.
+  \item $\mathcal{P}: \mathcal{S} \times \mathcal{A} \times \mathcal{S} \to [0, 1]$ is the state transition function, describing the probability of transitioning to a new state $s' \in \mathcal{S}$ given the current state $s \in \mathcal{S}$ and joint action $a \in \mathcal{A}$.
+  \item $\mathcal{R} = {\mathcal{R}^i}_{i \in N}$, where $\mathcal{R}^i: \mathcal{S} \times \mathcal{A} \to \mathbb{R}$ is the reward function for agent $i$.
+  \item $\gamma \in [0, 1]$ is the discount factor.
+\end{itemize}
+Each agent $i$ at time $t$ receives an observation $o^i_t \in \mathcal{O}^i$, 
+takes an action $a^i_t \in \mathcal{A}^i$ based on its local policy $\pi^i: \mathcal{O}^i \times \mathcal{A}^i \to [0,1]$, and receives a reward $r^i_{t+1} = \mathcal{R}^i(s_t, a_t)$. 
 %
 The global state evolves according to $\mathcal{P}$. 
-Agents can exchange information with their neighbors in $\mathcal{G}$ (or $\mathcal{G}t$ if the graph is time-varying). 
+Agents can exchange information with their neighbors in $\mathcal{G}$ 
+(or $\mathcal{G}t$ if the graph is time-varying). 
 %
@@
 
-Similar to the individual reward function, a global average reward function can be defined as $\bar{\mathcal{R}}(s, a) = \frac{1}{n} \sum_{i=1}^n \mathcal{R}^i(s,a)$, leading to a global average Q-value:
+%Similar to the individual reward function, a global average reward function can be defined as $\bar{\mathcal{R}}(s, a) = \frac{1}{n} \sum_{i=1}^n \mathcal{R}^i(s,a)$, leading to a global average Q-value:
 
-\[ \bar{Q}(s, a) = \mathbb{E}_{\pi} \left[ \sum_{t=0}^{\infty} \gamma^t \bar{\mathcal{R}}(s_t, a_t) | s_0 = s, a_0 = a \right] \]
+%\[ \bar{Q}(s, a) = \mathbb{E}_{\pi} \left[ \sum_{t=0}^{\infty} \gamma^t \bar{\mathcal{R}}(s_t, a_t) | s_0 = s, a_0 = a \right] \]
 
-where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy. 
-The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
-There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep q-learning algorithm.
+%where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy. 
+%The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
+There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep Q-learning algorithm.
 \subsubsection{Deep Q-Learning Formalization}
-deep q-learning utilizes a deep neural network, 
+deep Q-learning utilizes a deep neural network, 
 often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
@@
 For centralized training, the global state $s$ can be used as input. 
-The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., independent Q-learning, value decomposition methods).  
+The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., independent Q-learning, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).  
 For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: refiniments

@@
 \subsubsection{Deep Q-Learning Formalization}
-deep Q-learning utilizes a deep neural network, 
+Deep Q-learning~\cite{DBLP:conf/l4dc/FanWXY20} utilizes a deep neural network, 
 often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
@@
 For centralized training, the global state $s$ can be used as input. 
-The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., independent Q-learning, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).  
+The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
 For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
add ref to local picture

@@
 \usepackage{mytodonotes}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{cleveref}
 
@@
 \subsection{Learning Schemes}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-ctde.pdf}
+  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
+  \caption{Graphical rap presentation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
+  \label{fig:learning_paradigms}
+\end{figure}
 Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
-Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE).
+Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.
 

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add the pseudocode

@@
 \usepackage{mytodonotes}
+\usepackage[ruled,vlined]{algorithm2e}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% \author{Nicolò Malucelli}
-% \orcid{1234-5678-9012}
-% \affiliation{%
-%   \institution{University of Bologna}
-%   \streetaddress{Via dell'Università, 50}
-%   \city{Cesena} 
-%   \country{Italy}
-% }
-% \email{nicolo.malucelli@studio.unibo.it}
-
-% \author{Davide Domini}
-% \orcid{1234-5678-9012}
-% \affiliation{%
 %   \institution{University of Bologna}
@@
 %   \city{Cesena} 
-%   \country{Italy}
-% }
-% \email{gianluca.aguzzi@unibo.it}
+%   \country{Italy}\usepackage{algorithm}
 
-% \author{Mirko Viroli}
-% \affiliation{%
-%   \institution{University of Bologna}
-%   \streetaddress{Via dell'Università, 50}
-%   \city{Cesena} 
-%   \country{Italy}
-% }
-% \email{mirko.viroli@unibo.it}
-
-% % The default list of authors is too long for headers}
 % \renewcommand{\shortauthors}{N. Malucelli et al.}
@@
 
-\subsection{Nearest Neighboring Consensus}
+\subsection{K-Nearest Neighboring Consensus}
+In case of homogeneous agents (i.e., when all agents have the same action and observation space),
+the goal of learning is to find a common policy that all agents can follow.
+This approach is typically used in large-scale systems where agents are identical and need to reach a consensus---see [cite].
+%
+In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading to a consensus on the best policy.
+%
+In this way, each agent $i$ continue to learn independently, but at each iteration, it updates its Q-network using the Q-values of the best-performing agent in its neighborhood.
+
+The best performing agent is selected based on the average reward it has received in the last $n$ episodes.
+Formally, the update rule for agent $i$ at time $t+1$ is:
+\begin{equation}
+  \theta^{t+1}_i \leftarrow \theta^t_{\text{best}}
+\end{equation}
+where $\theta^t_{\text{best}}$ is the Q-network of the best-performing agent in the neighborhood $\mathcal{N}_k(i)$ at time $t$.
 
 \subsection{Experience Sharing}
+Experience sharing is a simple yet effective method for distributed learning.
+This approach is typically used in centralized training to improve sample efficiency and learning stability.
+In our distributed setting, each agent maintains its own experience replay buffer, but it also shares a fraction of its experiences with its neighbors.
+This allows agents to learn from each other's experiences, potentially accelerating learning and improving coordination because agents can learn from each other's mistakes and successes.
+%
+Formally, the reply buffer of agent $i$ at time $t$ is $\mathcal{D}^t_i = \{(o^i, a^i, r^i, o'^i)\}$.
+At each iteration, agent $i$ shares a fraction $\beta$ of its experiences with its neighbors in $\mathcal{N}_k(i)$.
+The update rule for agent $i$ at time $t+1$ is:
+\begin{equation}
+  \mathcal{D}^{t+1}_i = \mathcal{D}^t_i \cup \bigcup_{j \in \mathcal{N}_k(i)} \beta \mathcal{D}^t_j
+\end{equation}
+\subsection{Neighboring-Based Training with Deep Q-Learning}
+The neighboring-based training strategies can be integrated with deep Q-learning to enable distributed learning in multi-agent settings.
+%
+The algorithm follow the same structure as the deep Q-learning algorithm, but with the addition of the neighboring-based intereactions.
+%
+This may happen with a different frequency for each strategy, depending on the communication overhead and the desired level of coordination.
 
-\begin{itemize}
-\item Provide a detailed explanation of each neighbor-based method:
-\begin{itemize}
-\item \textbf{Independent learners:} Emphasize its simplicity and scalability but highlight its vulnerability to non-stationarity.
-\item \textbf{NN-Averaging:} Describe the weight averaging process, discuss the influence of neighbor selection and averaging frequency, and mention weighted averaging variations.
-\item \textbf{NN-Consensus:} Explain the selection of the best-performing network and its potential benefits and drawbacks.
-\item \textbf{Experience Sharing:} Detail how agents share experiences, discuss asynchronous vs. synchronous sharing, and highlight its advantages in sparse interaction environments.
-\end{itemize}
-\end{itemize}
+In [ref] we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
+\begin{algorithm}
+  \caption{Neighboring-Based Deep Q-Learning}
+  \label{alg:neighbor_dqn}
+  \ForEach{agent $i \in N$}{
+      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
+      Initialize replay buffer $\mathcal{B}^i$
+  }
+  \For{episode = 1 to M}{
+      \ForEach{agent $i \in N$}{
+          Initialize initial observation $o_0^i$
+      }
+      \For{t = 0 to T}{
+          \ForEach{agent $i \in N$}{
+              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
+              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
+              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{B}^i$\\
+              Sample a mini-batch from $\mathcal{B}^i$\\
+              Calculate target values using chosen neighboring strategy (see below)\\
+              Update $\theta^i$ by minimizing the TD error\\
+              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
+              \textbf{
+              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
+          }
+      }
+  }
+\end{algorithm}
+
 \section{Experimental Setup}\label{sec:experiments}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
adding something, i dunno what, i'm really tired and I want to rasengan
more in sota

@@
 Multi-agent reinforcement learning is a longstanding research area with a rich literature, starting 
-from seminal works like [cite ] and [cite] to more recent contributions like [cite] and [cite].
+from seminal works like~\cite{tan1993multi} and~\cite{busoniu2008comprehensive} to more recent contributions like~\cite{gronauer2022multi} and~\cite{canese2021multi}.
 %
@@
 
-In [ref] we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
+In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
 \begin{algorithm}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add discussion of independent learners

@@
 as the environment effectively changes from each agent's perspective.
+
 \subsection{State of the Art}
@@
 In the following, we briefly discuss some of the most relevant approaches in the field.
-\paragraph{Independent Learners}
+\subsubsection{Independent Learners}
+In independent learner, each agent learns its policy independently, disregarding the actions and policies of other agents. 
+This straightforward approach, among the earliest explored in MARL, often relies on variants of Q-learning. 
+However, independent learners struggle with coordination due to the non-stationarity introduced by the simultaneous learning of other agents.
 
+Several algorithms have attempted to address these coordination challenges within the independent learner paradigm. 
+Basic decentralized Q-learning~\cite{tan1993multi} allows each agent to learn its Q-values independently but often converges to suboptimal joint policies due to a lack of coordination. 
+Subsequent work introduced heuristic-based extensions to improve coordination.
+Approaches like distributed Q-learning~\cite{lauer2000algorithm} incorporate optimism in Q-value updates and equilibrium selection mechanisms to mitigate the convergence to shadowed equilibria (i.e., equilibria that are unstable due to the independent learning processes).
+Instead, algorithms such as hysteretic Q-learning~\cite{matignon2007hysteretic}, lenient Q-Learning~\cite{bloembergen2010lenient} and win-or-learn fast policy hill climbing~\cite{bowling2002multiagent} employ adaptive learning rates to address the issue of alternating exploration between agents, improving robustness and convergence.
+%
+Empirical comparisons of these algorithms highlight the trade-offs in performance across various MARL tasks and coordination challenges~\cite{matignon2012independent}. 
+While initially developed for tabular settings, some of these methods, like hysteretic Q-learning~\cite{palmer2017lenient} and lenient Q-learning, have been extended to deep reinforcement learning settings.
+However, these independent approaches, even with deep learning, often exhibit instability and slow convergence in complex environments and fundamentally lack explicit mechanisms for inter-agent coordination.
+Consequently, more sophisticated MARL algorithms have been developed that explicitly account for the interactions and policies of other agents to facilitate more effective coordination.
 \paragraph{Neighboring-Based Methods}

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add a todo on centralized actor critic approaches

@@
 \paragraph{Neighboring-Based Methods}
+Neighboring-based methods in MARL address the scalability and communication overhead challenges of fully centralized approaches by restricting agent interactions to a local neighborhood. 
+This introduces a structure where agents communicate and coordinate with a limited set of neighbors, reducing the complexity of joint action and policy learning.
+%
+One prominent category within neighboring-based methods is consensus-based algorithms. 
+These algorithms aim to reach a consensus among agents on shared values or policies through local information exchange. 
+Early work like QD-learning~\cite{kar2012qd} extends Q-learning with a consensus update term, 
+enabling agents to converge towards optimal Q-values despite only receiving local rewards.
+%  
+Recent advances in consensus-based MARL leverage deep learning and actor-critic architectures, 
+combining local policy updates with consensus updates on critic parameters or gradients, 
+as seen in the recent works~\cite{7434032,pennesi2010distributed,zhang2018fully,DBLP:journals/jmlr/CiosekW20}.
+
+These algorithms often exhibit improved scalability and communication efficiency compared to fully centralized methods, 
+but still need lack in capturing the global structure of the environment and the interactions between agents.
 \paragraph{Centralized Actor-Critic Methods}
-
+\gianlu{
+  todo -- discuss the main three solution, policy based (MAPPO, MADDPG, etc.), value based (QMIX, VDQN, etc.) and mean field (mean-q learning with field-informed RL).
+}
 \subsection{Motivation}

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
minors on abstract

@@
 %
-This paper investigates the effectiveness of various neighbor-based decentralized training strategies based on the well-known deep-q learning algorithm 
-  as a viable alternative to centralized training. 
+This paper investigates the effectiveness of various neighbor-based decentralized training strategies based 
+  on the well-known Deep-Q Learning algorithm as a viable alternative to centralized training. 
 %  
 We evaluate experience sharing, nearest neighboring averaging, and nearest neighboring consensus methods 
-  in a custom multi-agent environment and compare their performance against centralized training. 
+  in a custom multi-agent environment and compare their performance against centralized training
+  and totally decentralized training. 
 %  

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
fix typo sec 2

@@
 \subsubsection{Independent Learners}
-In independent learner, each agent learns its policy independently, disregarding the actions and policies of other agents. 
+In independent learners, each agent learns its policy independently, disregarding the actions and policies of other agents. 
 This straightforward approach, among the earliest explored in MARL, often relies on variants of Q-learning. 

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: same formulas

@@
       Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
-      Initialize replay buffer $\mathcal{B}^i$
+      Initialize replay buffer $\mathcal{D}^i$
   }
@@
               Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
-              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{B}^i$\\
-              Sample a mini-batch from $\mathcal{B}^i$\\
+              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
+              Sample a mini-batch from $\mathcal{D}^i$\\
               Calculate target values using chosen neighboring strategy (see below)\\

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
init eval setup and add some charts for results

@@
 \usepackage{mytodonotes}
+\usepackage{subcaption}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \end{algorithm}
+\section{Experimental Setup}\label{sec:experiments}
 
-\section{Experimental Setup}\label{sec:experiments}
-\begin{itemize}
-\item Introduce the custom "collect the items" multi-agent environment:
-\begin{itemize}
-\item Describe the environment's dynamics, agent goals, and challenges.
-\item Specify the action space (continuous and discrete) and observation space design.
-\item Explain the reward structure, emphasizing the components that encourage cooperation.
-\end{itemize}
-\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
-\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
-\item Define the evaluation metrics: average episode length and average reward.
-\end{itemize}
+To validate our approach, we developed a custom learning scenario using three State-of-the-Art frameworks 
+  in Reinforcement Learning and Deep Learning, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
+  (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
+  \emph{Gymnasium}~\cite{DBLP:journals/corr/abs-2407-17032}
+  and \emph{PyTorch}~\cite{DBLP:conf/nips/PaszkeGMLBCKLGA19}.
+
+First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
+  called \emph{collect the items} -- see \Cref{fig:env}.
+%
+This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
+ are randomly placed.
+%
+The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
+%
+% Action space
+%
+% Obseration space
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{figures/env.pdf}
+  \caption{Graphical representation of the environment. 
+  Specifically, the environment consists of a 2D euclidean space.
+  The blue dots represent the agents, while the yellow stars represent the items that 
+  the agents aim to collect.
+  }
+  \label{fig:env}
+\end{figure}
+
+% \begin{itemize}
+% \item Introduce the custom "collect the items" multi-agent environment:
+% \begin{itemize}
+% \item Describe the environment's dynamics, agent goals, and challenges.
+% \item Specify the action space (continuous and discrete) and observation space design.
+% \item Explain the reward structure, emphasizing the components that encourage cooperation.
+% \end{itemize}
+% \item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
+% \item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
+% \item Define the evaluation metrics: average episode length and average reward.
+% \end{itemize}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
+  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
+  \caption{Training results...}
+  \label{fig:results}
+\end{figure}
+
+\begin{figure*}[htb]
+  \centering
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{figures/mean-time-comparison-8-agents.pdf}
+      %\caption{Start of the simulation.}
+      % \label{fig:zones1}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{figures/mean-time-comparison-16-agents.pdf}
+      %\caption{After k time steps of the simulation.}
+      % \label{fig:zones2}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{figures/mean-time-comparison-32-agents.pdf}
+      %\caption{End of the simulation.}
+      % \label{fig:zones3}
+  \end{subfigure}
+  \caption{ To-do
+  }
+  \label{fig:time-eval}
+\end{figure*}
+
 \section{Conclusion}\label{sec:conclusion}

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
more on experimental eval

@@
 \usepackage{subcaption}
+\usepackage[inline]{enumitem}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 %
-% Action space
+In particular, each agent has an observation space defined by three main parameters, namely: 
+\begin{enumerate*}[label=(\roman*)]
+  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
+  \item number of closest items that the agent is able to see;
+  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
+    the evolution of the environment.
+\end{enumerate*} 
 %
-% Obseration space
+Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
+  (up, down and diagonal).
+
+% Reward
+
+% Specify the chosen RL algorithm (DQN) and its hyperparameter configuration
+
+% Define the evaluation metrics: average episode length and average reward
 
@@
 
-% \begin{itemize}
-% \item Introduce the custom "collect the items" multi-agent environment:
-% \begin{itemize}
-% \item Describe the environment's dynamics, agent goals, and challenges.
-% \item Specify the action space (continuous and discrete) and observation space design.
-% \item Explain the reward structure, emphasizing the components that encourage cooperation.
-% \end{itemize}
-% \item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
-% \item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
-% \item Define the evaluation metrics: average episode length and average reward.
-% \end{itemize}
+\begin{figure}
+  \centering
+  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
+  \caption{TODO
+  }
+  \label{fig:behavior}
+\end{figure}
 

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
update sota with centralized approaches

@@
 Many prominent approaches in this field employ a centralized training and decentralized execution paradigm
- (e.g., COMA~\cite{foerster2018counterfactual}, MAPPO~\cite{yu2022surprising}, MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17}, QMIX~\cite{DBLP:conf/icml/RashidSWFFW18}, QTRAN~\cite{DBLP:conf/icml/SonKKHY19}),
+ (e.g.,MAPPO~\cite{yu2022surprising}, MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17}, QMIX~\cite{DBLP:conf/icml/RashidSWFFW18}, QTRAN~\cite{DBLP:conf/icml/SonKKHY19}), 
  where a centralized learner trains distributed policies that are subsequently executed independently. 
@@
 }
+\paragraph{Centralized Actor-Critic Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
+leveraging centralized information during training to learn decentralized policies for execution. 
+This approach addresses the challenges of partial observability and non-stationarity while maintaining the scalability of decentralized execution. % 
+Actor-critic methods are well-suited for the CTDE paradigm, 
+where a centralized critic provides feedback to decentralized actors~\cite{DBLP:conf/icml/RashidSWFFW18,DBLP:journals/corr/SunehagLGCZJLSL17,yu2022surprising,DBLP:conf/nips/LoweWTHAM17}. 
+% 
+The most influential algorithms in this area are the one called policy-based methods (i.e., the ones that learn a policy directly).
+%
+Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates.
+Each agent then learns a deterministic policy based on its local observations. % 
+Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
+MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
+This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
+Another class of algorithms, called value-based methods, learn a value function that estimates the expected return for each agent.
+%
+Value Decomposition Networks (VDN)~\cite{DBLP:journals/corr/SunehagLGCZJLSL17} and QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} are representative algorithms in this category. 
+VDN factorizes the joint Q-function into a sum of individual agent Q-functions, simplifying the learning process. 
+QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
+allowing for more complex representations of joint action values. %
+
+Another approach to address the scalability challenge in MARL is \emph{mean field reinforcement learning}, i.e., the one that models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent.
+%
+In this context, mean field q-learning (Mean-Q)~\cite{DBLP:conf/icml/YangLLZZW18} has been proposed.
+This approach scales well to large numbers of agents and has been successful in various applications. 
+% 
+There are also modern solution which leverages collective abstraction to reduce the complexity of the problem, such as the one proposed in field-informed reinforcement learning.
 \subsection{Motivation}

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
add caption for fig3
fix typo caption fig1

@@
   \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
-  \caption{Graphical rap presentation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
+  \caption{Graphical representation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
   \label{fig:learning_paradigms}
@@
   \includegraphics[width=1\linewidth]{figures/behavior.pdf}
-  \caption{TODO
+  \caption{Graphical representation of wanted and unwanted behaviors.
+  On the left, the wanted behavior, the agents correctly cooperate to cover
+  two different items.
+  While, on the right, the agents do not correctly cooperate covering
+  the same item.
   }

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add self-cite (dom i'm a dog, I know)

@@
 but still need lack in capturing the global structure of the environment and the interactions between agents.
-\paragraph{Centralized Actor-Critic Methods}
-\gianlu{
-  todo -- discuss the main three solution, policy based (MAPPO, MADDPG, etc.), value based (QMIX, VDQN, etc.) and mean field (mean-q learning with field-informed RL).
-}
+
 \paragraph{Centralized Actor-Critic Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
@@
 % 
-There are also modern solution which leverages collective abstraction to reduce the complexity of the problem, such as the one proposed in field-informed reinforcement learning.
+There are also modern solution which leverages collective abstraction to reduce the complexity of the problem, such as the one proposed in field-informed reinforcement learning~\cite{DBLP:conf/acsos/AguzziVE23}.
 \subsection{Motivation}

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: minor on paragraph

@@
 
-\paragraph{Centralized Actor-Critic Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
+\paragraph{Centralized Training Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
 leveraging centralized information during training to learn decentralized policies for execution. 

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: massage on abstract

@@
 \begin{abstract}
-Multi-agent deep reinforcement learning (MADRL) is gaining popularity as a powerful extension of
-  single-agent reinforcement learning for training collaborative or competitive agents
-  in complex environments. 
+Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful extension of single-agent reinforcement learning, 
+enabling the training of both collaborative and competitive agents in complex environments. 
 %
-MADRL, however, introduces unique challenges, such as non-stationarity, partial observability, 
-  and credit assignment that complicate the learning process.
+The most widely adopted training paradigm in MADRL is centralized training with decentralized execution (CTDE), which has demonstrated significant effectiveness. 
 %
-Typically, in the literature, centralized training methods are used to tackle some of these challenges, 
-  although they often face scalability limitations as the number of agents grows.
+However, it relies on a centralized learner, requiring agents to learn in an offline setting and execute online. To address this limitation, decentralized training methods have been introduced. 
 %
-For this reason, decentralized training techniques have been proposed, however, 
-  generally they have a longer convergence time compared to centralized ones 
-  and may lead to instability.
+While these techniques offer greater flexibility, they tend to have slower convergence and can suffer from instability compared to centralized approaches.
 %

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
add reward description

@@
 
-First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
+\paragraph{Environment} First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
   called \emph{collect the items} -- see \Cref{fig:env}.
@@
 % Reward 
+\paragraph{Reward} One of the most important aspects in MARL is how the reward signal that the agents use to 
+  learn is defined.
+%
+In particular, we have defined a reward function composed of many subcomponents, namely:
+\begin{itemize}
+  \item Agents are penalized when their action area intersect. 
+  \[ \psi = \begin{cases}
+    0 & \text{if no intersections} \\
+    -2 \cdot |I_a| & \text{otherwise}
+  \end{cases} \]
+  \item Agents are penalized at each time step by a constant value $\sigma$ defined as
+    an hyperparameter.
+    \[ \zeta = - \sigma \]
+  \item Each agent $a$ is rewarded if it moves towards one of the visible target items.
+    \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
+    Where $p_a^t$ is the position of the agent $a$ at time t (similarly for $p_i^{t}$ regarding items),
+    $\delta$ is a scalar hyperparameter used to tune the importance of this component and
+    $V_{items}$ is the set of visible items.
+  \item Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
+    \[ \chi = \frac{1}{2|N_{a_i}|} \cdot \sum_{a_j \in N_{a_i}} d(p_{a_i}^{t+1}, p_{a_j}^{t+1}) - d(p_{a_i}^{t}, p_{a_j}^{t}) \]
+  \item Each agent is rewarded for any collected visible items ($C_i$) is the set of collected items), 
+    whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 
+    to develop cooperative behaviors.
+    \[ \rho = 100 \cdot |C_i| \]
+\end{itemize}
+The final reward is computed as the sum of all the subcomponents: 
+  \[ \psi + \zeta + \xi + \chi + \rho \]
 
 % Specify the chosen RL algorithm (DQN) and its hyperparameter configuration
+\paragraph{Learning algorithm}
 
 % Define the evaluation metrics: average episode length and average reward
+\paragraph{Evaluation metrics}
 

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
fix final reward
more details on reward
add eval metrics description

--- 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
@@
 
+\subsection{Environment} 
 First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
@@
 % Reward 
+\subsection{Reward}
+One of the most important aspects in MARL is how the reward signal that the agents use to 
+  learn is defined.
+%
+In particular, we have defined a reward function composed of many subcomponents.
+
+\paragraph{Collisions} Agents are penalized when their action area intersect. 
+  \[ \psi = \begin{cases}
+    0 & \text{if no intersections} \\
+    -2 \cdot |I_a| & \text{otherwise}
+  \end{cases} \]
+  Where $I_a$ is the set of agents with intersecting action area.
+
+\paragraph{Time step} Agents are penalized at each time step by a constant value $\sigma$ defined as
+    an hyperparameter.
+    \[ \zeta = - \sigma \]
+
+\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items.
+    \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
+    Where $p_a^t$ is the position of the agent $a$ at time t (similarly for $p_i^{t}$ regarding items),
+    $\delta$ is a scalar hyperparameter used to tune the importance of this component and
+    $V_{items}$ is the set of visible items.
+\paragraph{Moving away from agents} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
+    \[ \chi = \frac{1}{2|N_{a_i}|} \cdot \sum_{a_j \in N_{a_i}} d(p_{a_i}^{t+1}, p_{a_j}^{t+1}) - d(p_{a_i}^{t}, p_{a_j}^{t}) \]
+
+\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$) is the set of collected items), 
+    whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 
+    to develop cooperative behaviors.
+    \[ \rho = 100 \cdot |C_i| \]
+
+\paragraph{Final reward} The final reward is computed as the sum of all the subcomponents: 
+  \[ R = \psi + \zeta + \xi + \chi + \rho \]
 
 % Specify the chosen RL algorithm (DQN) and its hyperparameter configuration
+\subsection{Learning algorithm}
 
 % Define the evaluation metrics: average episode length and average reward
+\subsection{Evaluation metrics} 
+In our experiments, we employed two metrics to evaluate the performance of the learning
+  agents and monitor the quality of the training process, namely: 
+  \begin{enumerate*}[label=(\roman*)]
+    \item \emph{Mean Episode Reward}; and
+    \item \emph{Mean Episode Length}.
+  \end{enumerate*}
+
+\paragraph{Mean Episode Reward} 
+The Mean Episode Reward measures the average cumulative reward the agent obtains during each episode, 
+  serving as a direct indicator of how well each agent is performing in achieving its task.
+%
+Formally, for $N$ episodes, the mean reward $R_{mean}$ is computed as:
+  \[ R_{mean} = \frac{1}{N} \sum_{i=1}^{N} R_i \]
+  where $R_i$ is the total reward obtained in the $i$-th episode.
+
+\paragraph{Mean Episode Length}
+On the other hand, the Mean Episode Length represents the average number of time steps (or actions) 
+  the agent takes per episode before reaching the terminal state. 
+%
+It provides insights into the agent's efficiency in completing tasks, especially in environments 
+  where shorter episodes indicate better performance.
+%
+The mean episode length $L_{mean}$ is calculated as:
+  \[ L_{mean} = \frac{1}{N} \sum_{i=1}^{N} L_i \]
+  where $L_i$ is length of $i$-th episode.
 

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add learning algorithm description

@@
 
-% Specify the chosen RL algorithm (DQN) and its hyperparameter configuration
 \subsection{Learning algorithm}
+In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
+%
+We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
+  considered in the decision-making process.
+%
+A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
+  for long-term benefits, striking a balance between short-term and long-term planning.
+%
+We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
+%
+This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
+  the training process, specially in complex environments with multiple interacting agents.
+%
+For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
+  of experiences in each update. 
+%
+A smaller batch size could lead to noisier updates, while a larger one might slow down training without
+  significantly improving performance.
+%
+Additionally, we enabled two key features of the DQN algorithm, namely:
+  \begin{enumerate*}[label=(\roman*)]
+    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
+      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
+      the complex interactions between agents ; and
+    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
+      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
+      specific actions within that state.
+  \end{enumerate*}
 
-% Define the evaluation metrics: average episode length and average reward
 \subsection{Evaluation metrics} 

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add link to anonymous gh

@@
 \usepackage{subcaption}
+\usepackage{url}
 \usepackage[inline]{enumitem}
@@
 
+We ran a total of $35$ training experiments, namely: $5$ different methods 
+  (centralized, distributed and neighbor based approaches), and for each method we ran multiple experiments
+  varying the random seed (7 seeds) to obtain stronger results. 
+%
+Each experiment consisted of $50$ training episodes.
+
+Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
+  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
+  In this case, for each experiment we ran $100$ evaluation episodes.
+
+All the experiments are publicly available and reproducible\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
+
 \subsection{Environment} 
@@
 
-% Reward 
 \subsection{Reward}

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
on the paper flow

@@
 Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful extension of single-agent reinforcement learning, 
-enabling the training of both collaborative and competitive agents in complex environments. 
+enabling the training of both collaborative and competitive agents in several domains, like robotics, traffic management, and video games.
 %
@@
 %  
-We evaluate experience sharing, nearest neighboring averaging, and nearest neighboring consensus methods 
+We evaluate experience sharing, k-nearest neighboring averaging, and k-nearest neighboring consensus methods 
   in a custom multi-agent environment and compare their performance against centralized training
@@
 %
-In this direction, \emph{reinforcement learning} (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
+In this direction, \emph{reinforcement learning} (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents that interact with their environment and learn optimal policies through trial and error.
 %
@@
 %
-Recent advances in deep learning have further revolutionized the field, 
+Recent advances in deep learning have further advanced the field, 
 enabling the training of complex policies in high-dimensional state and action spaces, 
@@
 as demonstrated in various case studies involving video games~\cite{shao2019survey}, robotics~\cite{orr2023multi},
-and traffic management. 
+and traffic management~\cite{chu2019multi}. 
 %
@@
  where a centralized learner trains distributed policies that are subsequently executed independently. 
+%
 While facilitating decentralized runtime operation and avoiding single points of failure, 
@@
  followed by online execution with no further learning. 
- This inherent limitation hinders adaptation to changing environments or tasks at runtime.  
+ This inherent limitation hinders adaptation to changing environments or tasks at runtime, like those encountered in real-world robotics applications.  
 % 
@@
 %
-However, in many real-world multi-agent systems, 
- agents only interact with a limited subset of the overall system (also called \emph{networked agents}),
- as exemplified by limited sensing ranges in swarm robotics or localized interactions.  
- This observation also holds true in other natural systems, such as animal herds.
-%
-Therefore, 
-this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information.
+Inspired by many real-world multi-agent systems in which 
+ agents only interact with a limited subset of the overall system (also called \emph{networked agents})--as exemplified by limited sensing ranges in swarm robotics or localized interactions--in this paper proposes and formalizes a family of distributed learning methodologies based on neighborhood information.
 This approach aims to: 
@@
 The remainder of this paper is structured as follows.
-Section~\ref{sec:background} provides an overview of multi-agent reinforcement learning,
+\Cref{sec:background} provides an overview of multi-agent reinforcement learning,
 highlighting the key challenges and training paradigms.
-Section~\ref{sec:neighboring} introduces the proposed neighboring-based training strategies,
+\Cref{sec:neighboring} introduces the proposed neighboring-based training strategies,
 detailing their implementation and operation.
-Section~\ref{sec:experiments} presents the experimental setup and evaluation metrics.
-Section~\ref{sec:results} discusses the results of the experiments,
+\Cref{sec:experiments} presents the experimental setup and evaluation metrics.
+\Cref{sec:results} discusses the results of the experiments,
 comparing the performance of the neighboring-based methods against centralized training.
-Finally, Section~\ref{sec:conclusion} concludes the paper,
+Finally, \Cref{sec:conclusion} concludes the paper,
 summarizing the key findings and outlining potential future research directions.
@@
 
-In this paper, we focus on cooperative MADRL scenarios (so the deep version of MARL), 
+In this paper, we focus on cooperative MARL scenarios, 
 where agents must collaborate to achieve a common goal.
-In the following, we provide an overview of the key concepts in MADRL, 
+In the following, we provide an overview of the key concepts in MARL, 
 including the formalization of the problem, the deep Q-learning algorithm, and the training paradigms used in the literature.
 \subsection{Formalization}
-Since MADRL is a broad field, it is essential to provide a formalization to guide the discussion.
+Since MARL is a broad field, it is essential to provide a formalization to guide the discussion.
 In this paper, we consider partially observable networked markov decision process (PONMDP)~\cite{DBLP:journals/tac/AdlakhaLG12} as a tuple $(\mathcal{G}, \mathcal{S}, \mathcal{A}, \mathcal{O}, \mathcal{P}, \mathcal{R}, \gamma)$, where
@@
 
-In doing this, agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function or Q-value. 
+In doing this, agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function (also known as Q-value). 
 The latter represents the expected cumulative discounted reward the agent will receive by taking action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and then following its policy $\pi^i$:
@@
 %The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
-There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep Q-learning algorithm.
+Several algorithms aim to find the \emph{optimal} Q-value function, which maximizes the expected cumulative reward. One of the most popular among these is the Deep Q-learning algorithm.
 \subsubsection{Deep Q-Learning Formalization}
@@
 For centralized training, the global state $s$ can be used as input. 
-The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
-For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:
+The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed Deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
+For example, in independent Deep Q-learning--more details in \Cref{sec:sota}--each agent updates its Q-network independently using its local reward $r^i$:
 \begin{equation}
@@
 This process typically involves two phases:
-\begin{itemize}
-    \item \textbf{Offline training:} agents interact with a simulator or environment, 
-    gathering experience data used to update the central learner's policy.
-    \item \textbf{Online execution:} agents deploy the learned policy in the environment without further learning.
-\end{itemize}
+\begin{description}
+  \item[Offline training:] Agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
+  \item[Online execution:] Agents deploy the learned policy in the environment without further learning.
+\end{description}
 This approach offers several benefits.  
@@
 \paragraph{Decentralized Training with Decentralized Execution (DTDE)}
-DTDE eliminates the central learner; each agent learns independently. 
+DTDE eliminates the central learner; each agent learns independently from its own experiences.
 Inter-agent cooperation and communication can be incorporated during both training and execution. 
-Unlike CTDE, training and execution phases are not necessarily separate. 
-Simultaneous learning and execution allow for adaptation to changing environments or tasks at runtime.
+Unlike CTDE, training and execution phases are not necessarily separate---
+simultaneous learning and execution allow for adaptation to changing environments or tasks at runtime.
 %
@@
 
-\subsection{State of the Art}
-Multi-agent reinforcement learning is a longstanding research area with a rich literature, starting 
+\subsection{State of the Art}\label{sec:sota}
+MARL is a longstanding research area with a rich literature, starting 
 from seminal works like~\cite{tan1993multi} and~\cite{busoniu2008comprehensive} to more recent contributions like~\cite{gronauer2022multi} and~\cite{canese2021multi}.
 %
-In the following, we briefly discuss some of the most relevant approaches in the field.
+In the following, we briefly discuss some of the most relevant approaches in the field, which lead to the motivation for our work.
 \subsubsection{Independent Learners}
@@
 This straightforward approach, among the earliest explored in MARL, often relies on variants of Q-learning. 
-However, independent learners struggle with coordination due to the non-stationarity introduced by the simultaneous learning of other agents.
-
+%
 Several algorithms have attempted to address these coordination challenges within the independent learner paradigm. 
@@
 Consequently, more sophisticated MARL algorithms have been developed that explicitly account for the interactions and policies of other agents to facilitate more effective coordination.
-\paragraph{Neighboring-Based Methods}
+\subsubsection{Neighboring-Based Methods}
 Neighboring-based methods in MARL address the scalability and communication overhead challenges of fully centralized approaches by restricting agent interactions to a local neighborhood. 
@@
 %
-One prominent category within neighboring-based methods is consensus-based algorithms. 
+One prominent category within neighboring-based methods is \emph{consensus-based} algorithms. 
 These algorithms aim to reach a consensus among agents on shared values or policies through local information exchange. 
@@
 but still need lack in capturing the global structure of the environment and the interactions between agents.
-
-\paragraph{Centralized Training Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
+\subsubsection{Centralized Training Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
 leveraging centralized information during training to learn decentralized policies for execution. 
@@
 % 
-The most influential algorithms in this area are the one called policy-based methods (i.e., the ones that learn a policy directly).
+The most influential algorithms in this area are the one called \emph{policy-based} methods (i.e., the ones that learn a policy directly).
 %
@@
 MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
-This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
-Another class of algorithms, called value-based methods, learn a value function that estimates the expected return for each agent.
+%This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
+Another class of algorithms, called \emph{value-based} methods, learn a value function that estimates the expected return for each agent.
 %
 Value Decomposition Networks (VDN)~\cite{DBLP:journals/corr/SunehagLGCZJLSL17} and QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} are representative algorithms in this category. 
-VDN factorizes the joint Q-function into a sum of individual agent Q-functions, simplifying the learning process. 
+VDN factorizes the joint Q-function into a sum of individual agent Q-functions, 
+simplifying the learning process. 
 QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
 allowing for more complex representations of joint action values. % 
-
-Another approach to address the scalability challenge in MARL is \emph{mean field reinforcement learning}, i.e., the one that models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent.
+%
+Another approach to address the scalability challenge in MARL is \emph{mean field reinforcement learning}, i.e., 
+the one that models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent.
 %
@@
 %
-Neighbor-based methods have shown promise in simpler, tabular settings by enabling localized coordination,
+Neighbor-based methods have shown promise in simpler, 
+tabular settings by enabling localized coordination,
 but their integration with deep reinforcement learning remains largely unexplored. 
 This work bridges this gap by introducing a novel approach that combines the power of deep learning with the scalability of neighbor-based communication.  
-Our method aims to achieve both efficient decentralized learning and effective coordination, enabling online adaptation and robust performance in complex multi-agent environments.
+Our method aims to achieve both efficient decentralized learning and effective coordination, 
+enabling online adaptation and robust performance in complex multi-agent environments.
 \section{Neighboring-Based Distributed Learning Strategies}\label{sec:neighboring}
@@
 For this investigation, we focus on deep Q-learning as the underlying learning algorithm,
-and we consider the following strategies:
- k-nearest neighbor averaging, k-nearest neighbor consensus, and experience sharing.
+and we consider the following strategies: k-nearest neighbor averaging, k-nearest neighbor consensus, and experience sharing.
 
+\paragraph{K-Nearest Neighbor}
 Since these strategies are in general based on the notion of k-nearest neighbors,
@@
 This can be calculated, for instance, using Dijkstra's algorithm. 
-The length of a path is the sum of the weights of the edges along the path. If no path exists between $i$ and $j$, we set $d(i,j) = \infty$.
+The length of a path is the sum of the weights of the edges along the path. 
+If no path exists between $i$ and $j$, we set $d(i,j) = \infty$.
 %
@@
 
-\subsection{K-Nearest Neighbor Averaging}
+\paragraph{K-Nearest Neighbor Averaging}
 This approach averages an agent's Q-values with those of its nearest neighbors. 
@@
 
-\subsection{K-Nearest Neighboring Consensus}
+\paragraph{K-Nearest Neighboring Consensus}
 In case of homogeneous agents (i.e., when all agents have the same action and observation space),
 the goal of learning is to find a common policy that all agents can follow.
-This approach is typically used in large-scale systems where agents are identical and need to reach a consensus---see [cite].
+This approach is typically used in large-scale systems where agents are identical and need to reach a consensus---see~\cite{DBLP:conf/eusipco/BaldazoPZ19}.
 %
-In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading to a consensus on the best policy.
+In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading eventually to a consensus on the best same policy.
 %
 In this way, each agent $i$ continue to learn independently, but at each iteration, it updates its Q-network using the Q-values of the best-performing agent in its neighborhood.
-
+%
 The best performing agent is selected based on the average reward it has received in the last $n$ episodes.
@@
 
-\subsection{Experience Sharing}
+\paragraph{Experience Sharing}
 Experience sharing is a simple yet effective method for distributed learning.
-This approach is typically used in centralized training to improve sample efficiency and learning stability.
-In our distributed setting, each agent maintains its own experience replay buffer, but it also shares a fraction of its experiences with its neighbors.
-This allows agents to learn from each other's experiences, potentially accelerating learning and improving coordination because agents can learn from each other's mistakes and successes.
+This approach is typically used in centralized training to improve sample efficiency and learning stability~\cite{marl-book}.
+In our distributed setting, each agent maintains its own experience replay buffer, 
+but it also shares a fraction of its experiences with its neighbors.
+This allows agents to learn from each other's experiences, 
+potentially accelerating learning and improving coordination because agents can learn from each other's mistakes and successes.
 %
@@
 \end{equation}
-\subsection{Neighboring-Based Training with Deep Q-Learning}
+\paragraph{Neighboring-Based Training with Deep Q-Learning}
 The neighboring-based training strategies can be integrated with deep Q-learning to enable distributed learning in multi-agent settings.
 %
-The algorithm follow the same structure as the deep Q-learning algorithm, but with the addition of the neighboring-based intereactions.
+The algorithm follow the same structure as the deep Q-learning algorithm, 
+but with the addition of the neighboring-based intereactions.
 %
-This may happen with a different frequency for each strategy, depending on the communication overhead and the desired level of coordination.
+This may happen with a different frequency for each strategy, 
+depending on the communication overhead and the desired level of coordination.
 

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add caption figure 4

@@
   \includegraphics[width=1\linewidth]{figures/behavior.pdf}
-  \caption{Graphical representation of wanted and unwanted behaviors.
+  \caption{Wanted and unwanted behaviors.
   On the left, the wanted behavior, the agents correctly cooperate to cover
@@
 \section{Results and Evaluation}\label{sec:results}
-\begin{itemize}
-\item \textbf{Performance comparison:}
-\begin{itemize}
-\item Present the results of each distributed strategy against the centralized training baseline.
-\item Use graphs and statistical analysis to compare the average episode length and average reward.
-\item Highlight which neighbor-based methods perform comparably to centralized training.
-\end{itemize}
-\item \textbf{Scalability analysis:}
-\begin{itemize}
-\item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
-\item Show how each method scales with the increasing complexity, using appropriate visualizations.
-\item Discuss the implications of using pre-trained models with a larger number of agents.
-\end{itemize}
-\item \textbf{Communication overhead analysis:}
-\begin{itemize}
-\item Quantify the amount of information exchange for each strategy.
-\item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
-\item Discuss the trade-offs between performance and communication efficiency.
-\item Mention potential techniques for reducing communication overhead.
-\end{itemize}
-\end{itemize}
+
+% \begin{itemize}
+% \item \textbf{Performance comparison:}
+% \begin{itemize}
+% \item Present the results of each distributed strategy against the centralized training baseline.
+% \item Use graphs and statistical analysis to compare the average episode length and average reward.
+% \item Highlight which neighbor-based methods perform comparably to centralized training.
+% \end{itemize}
+% \item \textbf{Scalability analysis:}
+% \begin{itemize}
+% \item Describe how the experiments were modified to assess scalability (increasing agents, spawn area).
+% \item Show how each method scales with the increasing complexity, using appropriate visualizations.
+% \item Discuss the implications of using pre-trained models with a larger number of agents.
+% \end{itemize}
+% \item \textbf{Communication overhead analysis:}
+% \begin{itemize}
+% \item Quantify the amount of information exchange for each strategy.
+% \item Compare the communication overhead across different neighborhood sizes, possibly using graphs.
+% \item Discuss the trade-offs between performance and communication efficiency.
+% \item Mention potential techniques for reducing communication overhead.
+% \end{itemize}
+% \end{itemize}
 
@@
   \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
-  \caption{Training results...}
+  \caption{Data collected during training. 
+  We can see that DTDE method is highly unstable, while neighbor-based strategies perform 
+  comparably to CTDE.
+  }
   \label{fig:results}

### 2024-10-10 paper-2024-sac-marl-neighbouring-strategies.tex
add caption figure 5
update images for CTDE and DTDE

@@
   \centering
-  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-ctde.pdf}
-  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
+  \includegraphics[width=0.7\linewidth]{figures/CTDE.pdf}
+  \vskip 1 mm
+  \includegraphics[width=0.7\linewidth]{figures/DTDE.pdf}
   \caption{Graphical representation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
@@
   \end{subfigure}
-  \caption{ To-do
+  \caption{ Data collected during evaluation.
+  We can see how, increasing the number of agents, the DTDE methods become more unstable and takes more 
+  steps to solve the task, while neighbor-based strategies maintain -- on average -- results comparable to CTDE.
   }

### 2024-10-10 paper-2024-sac-marl-neighbouring-strategies.tex
add scalability chart
commented figure on env

@@
 First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
-  called \emph{collect the items} -- see \Cref{fig:env}.
+  called \emph{collect the items}. % -- see \Cref{fig:env}.
 %
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{figures/env.pdf}
-  \caption{Graphical representation of the environment. 
-  Specifically, the environment consists of a 2D euclidean space.
-  The blue dots represent the agents, while the yellow stars represent the items that 
-  the agents aim to collect.
-  }
-  \label{fig:env}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.7\linewidth]{figures/env.pdf}
+%   \caption{Graphical representation of the environment. 
+%   Specifically, the environment consists of a 2D euclidean space.
+%   The blue dots represent the agents, while the yellow stars represent the items that 
+%   the agents aim to collect.
+%   }
+%   \label{fig:env}
+% \end{figure}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=1\linewidth]{figures/scalability.pdf}
+  \caption{ Communication overhead due to different neighboring strategies.
+  }
+  \label{fig:scalability}
+\end{figure}
+
 \section{Conclusion}\label{sec:conclusion}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
pass till 2.3

@@
 \begin{abstract}
-Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful extension of single-agent reinforcement learning, 
-enabling the training of both collaborative and competitive agents in several domains, like robotics, traffic management, and video games.
+Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful paradigm for training intelligent agents in complex, multi-agent environments.
+%
+Extending beyond single-agent reinforcement learning, MADRL enables the development  of both collaborative and competitive agents in several domains, like robotics, traffic management, and video games.
 %
@@
 %
-However, it relies on a centralized learner, requiring agents to learn in an offline setting and execute online. To address this limitation, decentralized training methods have been introduced. 
+However, its reliance on a centralized learner necessitates that agents acquire policies offline and subsequently execute them online. 
+This inherent constraint motivates the exploration of decentralized training methodologies.
 %
@@
 %
-This paper investigates the effectiveness of various neighbor-based decentralized training strategies based 
+Therefore, this paper investigates the effectiveness of various neighbor-based decentralized training strategies based 
   on the well-known Deep-Q Learning algorithm as a viable alternative to centralized training. 
@@
 We evaluate experience sharing, k-nearest neighboring averaging, and k-nearest neighboring consensus methods 
-  in a custom multi-agent environment and compare their performance against centralized training
+  in a cooperative multi-agent environment and compare their performance against centralized training
   and totally decentralized training. 
@@
 \section{Background and Motivation}\label{sec:background}
-MARL is an extension of a sequential decision-making process, 
-where multiple \emph{agents} interact with each other and a shared \emph{environment}.
-In particular, each agent in the system aims to maximize its own \emph{reward signal} (i.e., a scalar feedback signal),
-which is typically a function of the global state (sometime not known, making the system \emph{partial observable}) and the joint action taken by all agents.
+Multi-agent reinforcement learning (MARL) involves a group of \emph{agents} interacting with a shared \emph{environment}. 
 %
-In doing that, each agent perceive the environment through its own \emph{observation function},
-which maps the global state to the agent's local observation and perform an action based on its \emph{policy} (i.e., a mapping from observations to actions).
+At each timestep, agents receive \emph{observations} and select \emph{actions} according to their individual \emph{policies} (mappings from observations to actions). 
 %
-This chosen action is then combined with the actions of other agents forming a \emph{joint action},
-which is used to update the global state and reward.
+These individual actions combine to form a \emph{joint action}, which influences the environment's transition to a new state. 
+%
+Each agent then receives a scalar \emph{reward} signal, typically a function of the global state and joint action. 
+%
+The goal of each agent is to maximize its cumulative reward. 
+%
+Environments can be \emph{partially observable}, meaning agents may not have access to the full global state, only receiving local observations through their respective \emph{observation functions}.
 
@@
 \[ J(\{\pi^i\}) = \lim_{T \to \infty} \mathbb{E} \left[ \frac{1}{T} \sum_{t=0}^{T-1} \frac{1}{N} \sum_{i \in \mathcal{N}} R^i(s_t, a_t) \right] \]
-
-In doing this, agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function (also known as Q-value). 
+Agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function (also known as \emph{Q-value}). 
 The latter represents the expected cumulative discounted reward the agent will receive by taking action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ and then following its policy $\pi^i$:
@@
 %The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
-Several algorithms aim to find the \emph{optimal} Q-value function, which maximizes the expected cumulative reward. One of the most popular among these is the Deep Q-learning algorithm.
+Several algorithms aim to find the \emph{optimal} Q-value function, which maximizes the expected cumulative reward. 
+%
+One of the most popular among these is the Deep Q-learning algorithm.
 \subsubsection{Deep Q-Learning Formalization}
@@
 This process typically involves two phases:
-\begin{description}
-  \item[Offline training:] Agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
-  \item[Online execution:] Agents deploy the learned policy in the environment without further learning.
-\end{description}
+\begin{itemize}
+  \item \textit{Offline training:} Agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
+  \item \textit{Online execution:} Agents deploy the learned policy in the environment without further learning.
+\end{itemize}
 This approach offers several benefits.  
@@
 Inter-agent cooperation and communication can be incorporated during both training and execution. 
-Unlike CTDE, training and execution phases are not necessarily separate---
-simultaneous learning and execution allow for adaptation to changing environments or tasks at runtime.
+Unlike CTDE, training and execution phases are not necessarily separate---simultaneous learning and execution allow for adaptation to 
+changing environments or tasks at runtime.
 %
@@
 %
-However, DTDE faces challenges. 
-Convergence time is often longer compared to centralized training. 
-The lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions. 
-Online learning in DTDE can introduce non-stationarity if agents do not account for other agents' evolving policies during training, 
+However, DTDE also presents several challenges to overcome, like: 
+i) convergence time is often longer compared to centralized training. 
+ii) The lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions; and 
+iii) online learning in DTDE can introduce non-stationarity if agents do not account for other agents' evolving policies during training, 
 as the environment effectively changes from each agent's perspective.

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: minor on the experimental setup

@@
 However, these independent approaches, even with deep learning, often exhibit instability and slow convergence in complex environments and fundamentally lack explicit mechanisms for inter-agent coordination.
-Consequently, more sophisticated MARL algorithms have been developed that explicitly account for the interactions and policies of other agents to facilitate more effective coordination.
+%Consequently, more sophisticated MARL algorithms have been developed that explicitly account for the interactions and policies of other agents to facilitate more effective coordination.
 \subsubsection{Neighboring-Based Methods}
 Neighboring-based methods in MARL address the scalability and communication overhead challenges of fully centralized approaches by restricting agent interactions to a local neighborhood. 
-This introduces a structure where agents communicate and coordinate with a limited set of neighbors, reducing the complexity of joint action and policy learning.
+This introduces agents communication and coordination with a limited set of neighbors, reducing the complexity of full joint action and policy learning.
 %
@@
 enabling online adaptation and robust performance in complex multi-agent environments.
+
 \section{Neighboring-Based Distributed Learning Strategies}\label{sec:neighboring}
@@
 
-\paragraph{K-Nearest Neighbor}
-Since these strategies are in general based on the notion of k-nearest neighbors,
-we first introduce this concept and then describe each strategy in detail.
+\paragraph{K-Nearest Neighbor Definition}
+The proposed strategies rely on the concept of k-nearest neighbors.
 Formally, consider a \emph{weighted} communication graph $\mathcal{G} = (N, E, W)$, where $N$ is the set of agents, where $W: E \rightarrow \mathbb{R}^+$ is a weight function assigning a positive weight to each edge.
@@
 \paragraph{K-Nearest Neighbor Averaging}
+\sloppy
 This approach averages an agent's Q-values with those of its nearest neighbors. 
@@
 
-To validate our approach, we developed a custom learning scenario using three State-of-the-Art frameworks 
-  in Reinforcement Learning and Deep Learning, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
+To validate our approach, we developed a custom learning scenario using three state-of-the-art frameworks 
+  in RL and DL, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
   (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
@@
 
-We ran a total of $35$ training experiments, namely: $5$ different methods 
-  (centralized, distributed and neighbor based approaches), and for each method we ran multiple experiments
-  varying the random seed (7 seeds) to obtain stronger results. 
+We ran a total of $35$ training experiments, 
+namely: $5$ different methods %% TODO check how many ex are discussed
+  (centralized, distributed and the three neighbor strategies discussed).
+Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.
 %

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: change the experimental setup label
chore: more on the simulated env

@@
 \end{algorithm}
-\section{Experimental Setup}\label{sec:experiments}
+\section{Experimental setup}\label{sec:experiments}
 
@@
 
-\subsection{Environment} 
-First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
-  called \emph{collect the items}. % -- see \Cref{fig:env}.
+\subsection{Simulated environment}
+The proposed multi-agent environment, which we design to evaluate the efficacy of the neighboring-based strategies,
+ consists of a two-dimensional Euclidean space 
+ populated by a variable number of \emph{targets} and \emph{agents}, 
+ whose initial positions are randomly distributed across the space.
 %
-This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
- are randomly placed.
+The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
 %
-The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
-%
-In particular, each agent has an observation space defined by three main parameters, namely: 
+The observation space of each agent consist of a tuple of three elements: %% TODO CHECK AGAIN
 \begin{enumerate*}[label=(\roman*)]
-  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
-  \item number of closest items that the agent is able to see;
+  \item number of the closest agents that the agent is able to see (thus, forming a neighborhood);
+  \item number of the closest items that the agent is able to see;
   \item memory of past states, thus encoding also temporal information, helping each agent to understand 
@@
 %
-Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
-  (up, down and diagonal).
+The action space for each agent is discrete, 
+consisting of eight possible movements corresponding 
+to the cardinal and diagonal directions on a grid
 
+This setup was chosen as it presents a challenging coordination problem that requires agents to learn both individual target-seeking behaviors and collaborative strategies for reducing the overall retrivial time,
+offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
 \subsection{Reward}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: pass on rewards

@@
 offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
-\subsection{Reward}
-One of the most important aspects in MARL is how the reward signal that the agents use to 
-  learn is defined.
-%
-In particular, we have defined a reward function composed of many subcomponents.
-
-\paragraph{Collisions} Agents are penalized when their action area intersect. 
+\subsubsection{Reward function}
+In the proposed environment, we design a reward function that both consider the individual performance of each agent (e.g., avoid collision) and the global performance of the team (e.g., collect items in the shortest time possible).
+In the following, we describe the components of the reward function:
+\paragraph{Collisions} Agents are penalized when their action area intersect. This penalty is proportional to the number of agents involved in a collision:
   \[ \psi = \begin{cases}
@@
   \end{cases} \]
-  Where $I_a$ is the set of agents with intersecting action area.
+where $I_a$ is the set of agents with intersecting action area.
 
 \paragraph{Time step} Agents are penalized at each time step by a constant value $\sigma$ defined as
-    an hyperparameter.
+    an hyperparameter, to encourage them to complete the task as quickly as possible.
     \[ \zeta = - \sigma \]
 
-\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items.
+\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items, discouraging agents from wandering aimlessly.
     \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
@@
 \paragraph{Moving away from agents} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
+This strategy encourages agents to avoid clustering and explore the environment more effectively.
     \[ \chi = \frac{1}{2|N_{a_i}|} \cdot \sum_{a_j \in N_{a_i}} d(p_{a_i}^{t+1}, p_{a_j}^{t+1}) - d(p_{a_i}^{t}, p_{a_j}^{t}) \]
 
-\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$) is the set of collected items), 
+\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$ is the set of collected items), 
     whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: remove DQN variations

@@
 %
-Additionally, we enabled two key features of the DQN algorithm, namely:
-  \begin{enumerate*}[label=(\roman*)]
-    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
-      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
-      the complex interactions between agents ; and
-    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
-      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
-      specific actions within that state.
-  \end{enumerate*}
+%Additionally, we enabled two key features of the DQN algorithm, namely:
+%  \begin{enumerate*}[label=(\roman*)]
+%    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
+%      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
+%      the complex interactions between agents ; and
+%    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
+%      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
+%      specific actions within that state.
+%  \end{enumerate*}
 
@@
   \includegraphics[width=1\linewidth]{figures/behavior.pdf}
-  \caption{Wanted and unwanted behaviors.
-  On the left, the wanted behavior, the agents correctly cooperate to cover
-  two different items.
-  While, on the right, the agents do not correctly cooperate covering
-  the same item.
-  }
+  \caption{Examples of cooperative and uncoordinated behavior.
+(Left) desired, agents effectively choose different paths to collect different items.
+(Right) undesired, agents cover the same path to collect the same item.}
   \label{fig:behavior}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add performance comparison and scalability

@@
 
+\paragraph{Performance comparison}
+The results -- \Cref{fig:results} -- shows that employing a centralized training (i.e., CTDE) approach allows the model to converge 
+ more rapidly -- in terms of episodes -- to a higher reward compared to a fully decentralized approach (i.e., DTDE). 
+%
+This difference becomes even more evident when considering the Mean Episode Length metric, where CTDE not only converges 
+ faster but also solves the task using shorter episodes than DTDE.
+
+Additionally, we implemented another state-of-the-art algorithm, namely MAPPO, as a baseline for comparison. 
+%
+However, MAPPO performed worse than both CTDE and DTDE across both metrics -- yielding lower results and exhibiting less stability, 
+ as reflected in its higher standard deviation.
+
+Regarding the proposed neighbor-based approaches, it can be observed that both \emph{experience sharing} and 
+ \emph{NN averaging} enhance the performance of DTDE, achieving results comparable to CTDE while also increasing 
+ learning stability. 
+% 
+On the other hand, \emph{NN consensus} maintains performance levels similar to DTDE, which may be attributed to the 
+ simplicity of the implemented consensus policy. 
+%
+Nevertheless, it remains more stable and achieves better performance than MAPPO.
+
+\paragraph{Scalability}
+To evaluate the scalability of the learned policies, we conducted several experiments by increasing the number 
+ of agents -- specifically to 8, 16, and 32 -- and measuring the time required to complete the task 
+ (i.e., mean episode length).
+
+The results -- \Cref{fig:time-eval} -- show that as the number of agents increases, DTDE exhibits both a higher mean time 
+ to solve the task and greater instability. 
+%
+In contrast, CTDE, NN averaging, and experience sharing maintain strong performance. 
+%
+Similar to the training phase, NN consensus does not achieve the same results as the other two neighbor-based 
+ approaches but remains on par with DTDE in terms of performance.
+
+\paragraph{Communication overhead}
+
 % \begin{itemize}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: more on the environment

@@
 %
+The environment is considered solved when all targets are collected, terminating the episode. 
+To prevent infinitely long episodes, a maximum time limit of T = 300 steps is imposed. 
+If all items are collected before this limit, the episode terminates early.
 The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
@@
 consisting of eight possible movements corresponding 
-to the cardinal and diagonal directions on a grid
+to the cardinal and diagonal directions on a grid.
+%
 
@@
   \begin{enumerate*}[label=(\roman*)]
-    \item \emph{Mean Episode Reward}; and
-    \item \emph{Mean Episode Length}.
+    \item \emph{Mean Episode Reward} ($R_{mean}$); and
+    \item \emph{Mean Episode Length} ($L_{mean}$).
   \end{enumerate*} 
-
-\paragraph{Mean Episode Reward} 
-The Mean Episode Reward measures the average cumulative reward the agent obtains during each episode, 
+%
+$R_{mean}$ measures the average cumulative reward the agent obtains during each episode, 
   serving as a direct indicator of how well each agent is performing in achieving its task.
@@
   \[ R_{mean} = \frac{1}{N} \sum_{i=1}^{N} R_i \]
-  where $R_i$ is the total reward obtained in the $i$-th episode.
+  where $R_i$ is the total reward obtained by all agents in the $i$-th episode. 
+  Formally, for a certain episode $i$, composed of $n$ agents, last $T$ time steps, the total reward $R_i$ is calculated as:
+  \[ R_i = \sum_{t=0}^{T} \sum_{j=1}^{n} r^j_t \]
+  where $r^j_t$ is the reward obtained by agent $j$ at time step $t$.
 
-\paragraph{Mean Episode Length}
-On the other hand, the Mean Episode Length represents the average number of time steps (or actions) 
-  the agent takes per episode before reaching the terminal state. 
+On the other hand, the $L_{mean}$ represents the average number of time steps needed to reaching the terminal state, i.e., no more items to collect. 
 %

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
paper restructure

@@
 \end{algorithm}
-\section{Experimental setup}\label{sec:experiments}
-
-To validate our approach, we developed a custom learning scenario using three state-of-the-art frameworks 
-  in RL and DL, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
-  (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
-  \emph{Gymnasium}~\cite{DBLP:journals/corr/abs-2407-17032}
-  and \emph{PyTorch}~\cite{DBLP:conf/nips/PaszkeGMLBCKLGA19}.
-
-We ran a total of $35$ training experiments, 
-namely: $5$ different methods %% TODO check how many ex are discussed
-  (centralized, distributed and the three neighbor strategies discussed).
-Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.
-%
-Each experiment consisted of $50$ training episodes.
-
-Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
-  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
-  In this case, for each experiment we ran $100$ evaluation episodes.
-
-All the experiments are publicly available and reproducible\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
-
+\section{Evaluation}\label{sec:experiments}
 \subsection{Simulated environment}
@@
   \[ R = \psi + \zeta + \xi + \chi + \rho \]
+
+\subsection{Experimental setup}
+To validate our approach, we developed a custom learning scenario using three state-of-the-art frameworks 
+  in RL and DL, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
+  (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
+  \emph{Gymnasium}~\cite{DBLP:journals/corr/abs-2407-17032}
+  and \emph{PyTorch}~\cite{DBLP:conf/nips/PaszkeGMLBCKLGA19}.
+
+We ran a total of $35$ training experiments, 
+namely: $5$ different methods %% TODO check how many ex are discussed
+  (centralized, distributed and the three neighbor strategies discussed).
+Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.
+%
+Each experiment consisted of $50$ training episodes. 
+%
+Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
+  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
+  In this case, for each experiment we ran $100$ evaluation episodes.
+All the experiments are publicly available and reproducible\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
 
@@
 
-\section{Results and Evaluation}\label{sec:results}
+\subsection{Results}\label{sec:results}
 

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: on restructuring, remove information from experimental setup

@@
 \section{Evaluation}\label{sec:experiments}
+This section presents the experimental setup and evaluation metrics used to assess the performance of the proposed neighboring-based training strategies.
+All the experiments and data produced are reproducible and publicly available\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
 \subsection{Simulated environment}
@@
 \subsection{Experimental setup}
-To validate our approach, we developed a custom learning scenario using three state-of-the-art frameworks 
-  in RL and DL, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
+The described environment was implemented using the \emph{Gymnasium} framework~\cite{DBLP:journals/corr/abs-2407-17032}.
+Moreover, we employed the following libraries to implement the learning algorithms namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
   (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
-  \emph{Gymnasium}~\cite{DBLP:journals/corr/abs-2407-17032}
   and \emph{PyTorch}~\cite{DBLP:conf/nips/PaszkeGMLBCKLGA19}.
@@
   In this case, for each experiment we ran $100$ evaluation episodes.
-All the experiments are publicly available and reproducible\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
 

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add communication overhead

@@
 
+The proposed neighbor-based approaches, particularly NN averaging and experience sharing, achieve performance
+ comparable to CTDE while maintaining a decentralized learning structure similar to DTDE. 
+% 
+However, this entails a communication overhead due to the information agents must exchange with their neighbors. 
+%
+For NN consensus, the overhead remains constant, as each agent selects the best neighbor and only exchanges 
+ information with that agent, meaning the amount of data shared does not increase with the number of neighbors. 
+% 
+In contrast, for NN averaging and experience sharing, the overhead scales linearly. 
+%
+Specifically, the growth in overhead for experience sharing is minimal, as the agents' experiences require very 
+ little memory. 
+%
+For NN averaging, however, this increase is more significant, as even a moderately complex neural network 
+ has a substantially larger memory footprint.
+% 
+Nevertheless, for all approaches, the overhead remains within a few megabytes (less than 25MB) when dealing with 
+ up to 10 neighboring agents.
+%
+This makes all approaches feasible, although in scenarios with limited communication resources, experience 
+ sharing would be the optimal choice, as it provides performance similar to NN averaging but with 
+ much lower overhead.
+
 % \begin{itemize}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add communication overhead figure ref
update caption fig 3

@@
 % 
-However, this entails a communication overhead due to the information agents must exchange with their neighbors. 
+However, this entails a communication overhead due to the information agents must exchange with their neighbors
+ -- see \Cref{fig:scalability}. 
 %
@@
   \caption{Data collected during training. 
-  We can see that DTDE method is highly unstable, while neighbor-based strategies perform 
-  comparably to CTDE.
+  We can see that two of the three neighbor-based strategies achieve performance similar to CTDE.
   }

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add conclusions

@@
 \section{Conclusion}\label{sec:conclusion}
-\begin{itemize}
-\item Summarize the key findings of the paper.
-\item Emphasize the viability of neighbor-based methods as alternatives to centralized training in MARL.
-\item Discuss the trade-offs observed in terms of performance, scalability, and communication overhead.
-\item Suggest potential directions for future research, such as exploring hybrid approaches or more advanced communication protocols.
-\end{itemize}
+This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE )with performance 
+ comparable to centralized approaches (i.e., CTDE). 
+%
+These strategies offer the flexibility of DTDE while retaining the stability and performance of CTDE. 
+%
+Specifically, we introduce three approaches, namely: NN Averaging, NN Consensus and Experience Sharing
+ which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
+%
+The results show that two of the three proposed methods significantly enhance DTDE performance, achieving outcomes comparable 
+ to CTDE, while NN consensus falls short of this goal, maintaining performance similar to DTDE. 
+%
+Furthermore, we analyzed the communication overhead, demonstrating that it remains minimal across all cases, 
+ particularly with experience sharing, making it suitable for scenarios with very limited communication resources.
+
+Future works may include several promising directions, namely:
+\begin{enumerate*}[label=(\roman*)]
+  \item explore the implementation of more advanced consensus algorithms to determine if this strategy can also achieve 
+   results comparable to the other two;
+  \item develop more sophisticated communication protocols to further reduce communication overhead; and
+  \item test these approaches in a wider range of, and more complex, scenarios than the one considered in this paper.
+\end{enumerate*}
 

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
fix experimental setup

@@
 
-We ran a total of $35$ training experiments, 
-namely: $5$ different methods %% TODO check how many ex are discussed
-  (centralized, distributed and the three neighbor strategies discussed).
+We ran a total of $42$ training experiments, 
+namely: $6$ different methods %% TODO check how many ex are discussed
+  (centralized, distributed and the three neighbor-based strategies discussed).
 Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
fix title paragraph nn consensus

@@
 
-\paragraph{K-Nearest Neighboring Consensus}
+\paragraph{K-Nearest Neighbor Consensus}
 In case of homogeneous agents (i.e., when all agents have the same action and observation space),

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: rewrite 4.1

@@
 \subsection{Simulated environment}
-The proposed multi-agent environment, which we design to evaluate the efficacy of the neighboring-based strategies,
- consists of a two-dimensional Euclidean space 
- populated by a variable number of \emph{targets} and \emph{agents}, 
- whose initial positions are randomly distributed across the space.
+The proposed multi-agent environment is a variant of the ``gather the items'' scenario, designed to study the impact of neighborhood strategies. 
+It consists of a 2D Euclidean space populated by $A$ agents and $T$ targets, 
+initially placed at random locations.
 %
-The environment is considered solved when all targets are collected, terminating the episode. 
-To prevent infinitely long episodes, a maximum time limit of T = 300 steps is imposed. 
-If all items are collected before this limit, the episode terminates early.
-The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
+The objective is for the agents to collectively capture all targets, 
+at which point the environment episode terminates successfully.  
+A maximum time limit of $T_{max} = 300$ time steps is enforced to prevent indefinite episodes.
+
+At each time step $t$, each agent $a$ receives an observation $o_a^t$ composed of the following elements:
+\begin{itemize}
+  \item \emph{Neighborhood perception}:  Agent $a$ perceives the relative positions (distance and direction) of its $A_v$ nearest neighboring agents. 
+  This information is represented as a set $\mathcal{V}_a^t = \{(d_{aj}^t, \theta_{aj}^t) | j \in \text{Nearest } A_v \text{ agents}\}$, 
+  where $d_{aj}^t$ is the Euclidean distance between agent $a$ and agent $j$ at time $t$, and $\theta_{aj}^t$ is the angle between the vector pointing from agent $a$ to agent $j$ and a fixed reference axis.
+  \item \emph{Target perception}: Agent $a$ perceives the relative positions (distance and direction) of its $T_v$ nearest targets. 
+  This is represented as a set $\mathcal{T}_a^t = \{(d_{ak}^t, \theta_{ak}^t) | k \in \text{Nearest } T_v \text{ targets}\}$, with $d_{ak}^t$ and $\theta_{ak}^t$ defined analogously to the neighborhood perception.
+  \item \emph{Memory}: Agent $a$ maintains a memory $\mathcal{H}_a^t$ of past perceptions, storing the neighborhood and target perceptions from the previous $H_t$ time steps.
+Formally, $\mathcal{H}_a^t = \{\mathcal{N}_a^{t-\tau}, \mathcal{T}_a^{t-\tau} | \tau = 1, \dots, H_t\}$.
+  This can be represented as a tensor of shape $(H_t, A_v + T_v, 2)$, where the last dimension represents the relative distance and angle for each perceived agent or target.
+\end{itemize}
+The complete observation $o_a^t$ at time $t$ for agent $a$ is thus given by $o_a^t = (\mathcal{N}_a^t, \mathcal{T}_a^t, \mathcal{H}_a^t)$.
+
+Communication between agents is restricted to a neighborhood $\mathcal{C}_a^t \subseteq \mathcal{N}_a^t$ 
+and depends on a communication graph $\mathcal{G}$.
 %
-The observation space of each agent consist of a tuple of three elements: %% TODO CHECK AGAIN
-\begin{enumerate*}[label=(\roman*)]
-  \item number of the closest agents that the agent is able to see (thus, forming a neighborhood);
-  \item number of the closest items that the agent is able to see;
-  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
-    the evolution of the environment.
-\end{enumerate*} 
+This communication enables the exchange of information such as Q-values or experiences 
+using on of the neighboring-based strategies discussed in \Cref{sec:neighboring}.
 %
-The action space for each agent is discrete, 
-consisting of eight possible movements corresponding 
-to the cardinal and diagonal directions on a grid.
+The action space for each agent is discrete, consisting of eight possible movements corresponding to the cardinal and diagonal directions on a grid.
+
+This environment provides a challenging coordination problem, 
+requiring agents to learn individual target-seeking behaviors and collaborative strategies 
+to minimize retrieval time. 
 %
-
-This setup was chosen as it presents a challenging coordination problem that requires agents to learn both individual target-seeking behaviors and collaborative strategies for reducing the overall retrivial time,
-offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
+It serves as a suitable testbed for evaluating the effectiveness 
+of neighbor-based decentralized training approaches.
 \subsubsection{Reward function}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: remove example of independent q learning
shrink: remove the formula for expressing the maximization of the return (it is discussed on dqn. it can be enough for this paper

@@
 or some global reward function like the average reward over all agents.
-Formally, it can be defined as:
-\[ J(\{\pi^i\}) = \lim_{T \to \infty} \mathbb{E} \left[ \frac{1}{T} \sum_{t=0}^{T-1} \frac{1}{N} \sum_{i \in \mathcal{N}} R^i(s_t, a_t) \right] \]
+%Formally, it can be defined as:
+%\[ J(\{\pi^i\}) = \lim_{T \to \infty} \mathbb{E} \left[ \frac{1}{T} \sum_{t=0}^{T-1} \frac{1}{N} \sum_{i \in \mathcal{N}} R^i(s_t, a_t) \right] \]
 Agents typically use other function to estimate the value of taking an action in a given state, such as the action-value function (also known as \emph{Q-value}). 
@@
 The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed Deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
-For example, in independent Deep Q-learning--more details in \Cref{sec:sota}--each agent updates its Q-network independently using its local reward $r^i$:
-\begin{equation}
-  \resizebox{\linewidth}{!}{$
-  \mathcal{L}^i(\theta^i) = \mathbb{E}_{(o^i, a^i, r^i, o'^i) \sim \mathcal{D}^i} \left[ \left( r^i + \gamma \max_{a'^i} Q^i(o'^i, a'^i; \theta^{i-}) - Q^i(o^i, a^i; \theta^i) \right)^2 \right]
-  $}
-  \end{equation}
+%For example, in independent Deep Q-learning--more details in \Cref{sec:sota}--each agent updates its Q-network independently using its local reward $r^i$:
+%\begin{equation}
+%  \resizebox{\linewidth}{!}{$
+%  \mathcal{L}^i(\theta^i) = \mathbb{E}_{(o^i, a^i, r^i, o'^i) \sim \mathcal{D}^i} \left[ \left( r^i + \gamma \max_{a'^i} Q^i(o'^i, a'^i; \theta^{i-}) - Q^i(o^i, a^i; \theta^i) \right)^2 \right]
+%  $}
+%  \end{equation}
 %\subsection{Key Concepts}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink algo description

@@
 
-In this paper, we focus on cooperative MARL scenarios, 
-where agents must collaborate to achieve a common goal.
-In the following, we provide an overview of the key concepts in MARL, 
-including the formalization of the problem, the deep Q-learning algorithm, and the training paradigms used in the literature.
+%In this paper, we focus on cooperative MARL scenarios, 
+%where agents must collaborate to achieve a common goal.
+%In the following, we provide an overview of the key concepts in MARL, 
+%including the formalization of the problem, the deep Q-learning algorithm, and the training paradigms used in the literature.
 \subsection{Formalization}
@@
 The objective is typically to maximize the expected discounted sum of rewards $\sum{t=0}^{\infty} \gamma^t r^i_t$ for each agent $i$, 
-or some global reward function like the average reward over all agents.
+or some global reward function like the average reward over all agents in case of cooperative scenarios.
 %Formally, it can be defined as:
@@
 This process typically involves two phases:
-\begin{itemize}
+\begin{enumerate}
   \item \textit{Offline training:} Agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
   \item \textit{Online execution:} Agents deploy the learned policy in the environment without further learning.
-\end{itemize}
+\end{enumerate}
 This approach offers several benefits.  
@@
               \textbf{
-              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
+              Every S steps, perform neighboring strategy}
           }
@@
   \centering
-  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
+  \includegraphics[width=0.7\linewidth]{figures/behavior.pdf}
   \caption{Examples of cooperative and uncoordinated behavior.

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: dtde e ctde images
shrink: discussion on independent learners

@@
   \centering
-  \includegraphics[width=0.7\linewidth]{figures/CTDE.pdf}
-  \vskip 1 mm
-  \includegraphics[width=0.7\linewidth]{figures/DTDE.pdf}
-  \caption{Graphical representation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
+  \includegraphics[width=0.49\linewidth]{figures/CTDE.pdf}
+  %\vskip 1 mm
+  \includegraphics[width=0.49\linewidth]{figures/DTDE.pdf}
+  \caption{Graphical representation of CTDE (left) and DTDE (right) in MARL.}
   \label{fig:learning_paradigms}
@@
 Basic decentralized Q-learning~\cite{tan1993multi} allows each agent to learn its Q-values independently but often converges to suboptimal joint policies due to a lack of coordination. 
-Subsequent work introduced heuristic-based extensions to improve coordination.
-Approaches like distributed Q-learning~\cite{lauer2000algorithm} incorporate optimism in Q-value updates and equilibrium selection mechanisms to mitigate the convergence to shadowed equilibria (i.e., equilibria that are unstable due to the independent learning processes).
-Instead, algorithms such as hysteretic Q-learning~\cite{matignon2007hysteretic}, lenient Q-Learning~\cite{bloembergen2010lenient} and win-or-learn fast policy hill climbing~\cite{bowling2002multiagent} employ adaptive learning rates to address the issue of alternating exploration between agents, improving robustness and convergence.
+%Subsequent work introduced heuristic-based extensions to improve coordination.
+%Approaches like distributed Q-learning~\cite{lauer2000algorithm} incorporate optimism in Q-value updates and equilibrium selection mechanisms to mitigate the convergence to shadowed equilibria (i.e., equilibria that are unstable due to the independent learning processes).
+%Instead, algorithms such as hysteretic Q-learning~\cite{matignon2007hysteretic}, lenient Q-Learning~\cite{bloembergen2010lenient} and win-or-learn fast policy hill climbing~\cite{bowling2002multiagent} employ adaptive learning rates to address the issue of alternating exploration between agents, improving robustness and convergence.
 %
-Empirical comparisons of these algorithms highlight the trade-offs in performance across various MARL tasks and coordination challenges~\cite{matignon2012independent}. 
+%Empirical comparisons of these algorithms highlight the trade-offs in performance across various MARL tasks and coordination challenges~\cite{matignon2012independent}. 
+Subsequent work introduced heuristic-based extensions to improve coordination, like distributed Q-learning~\cite{lauer2000algorithm}, hysteretic Q-learning~\cite{matignon2007hysteretic}, lenient Q-Learning~\cite{bloembergen2010lenient}, however empirical comparisons of these algorithms highlight the trade-offs in performance across various MARL tasks and coordination challenges~\cite{matignon2012independent}.
 While initially developed for tabular settings, some of these methods, like hysteretic Q-learning~\cite{palmer2017lenient} and lenient Q-learning, have been extended to deep reinforcement learning settings.

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: sota

@@
 The most influential algorithms in this area are the one called \emph{policy-based} methods (i.e., the ones that learn a policy directly).
+In this family, the most popular algorithms are MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{yu2022surprising}.
 %
-Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates.
-Each agent then learns a deterministic policy based on its local observations. % 
-Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
-MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
+%Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates.
+%Each agent then learns a deterministic policy based on its local observations. % 
+%Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
+%MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
 %This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
-Another class of algorithms, called \emph{value-based} methods, learn a value function that estimates the expected return for each agent.
+Another class of algorithms, called \emph{value-based} methods, learn a value function that estimates the expected return from a global point of view while maintaining decentralized policies.
 %
 Value Decomposition Networks (VDN)~\cite{DBLP:journals/corr/SunehagLGCZJLSL17} and QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} are representative algorithms in this category. 
-VDN factorizes the joint Q-function into a sum of individual agent Q-functions, 
-simplifying the learning process. 
-QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
-allowing for more complex representations of joint action values. % 
+%VDN factorizes the joint Q-function into a sum of individual agent Q-functions, 
+%simplifying the learning process. 
+%QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
+%allowing for more complex representations of joint action values. % 
 %
 Another approach to address the scalability challenge in MARL is \emph{mean field reinforcement learning}, i.e., 
-the one that models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent.
+it models the interaction between agents through a mean field, simplifying the multi-agent problem into a single-agent problem against an average opponent~\cite{DBLP:conf/icml/YangLLZZW18}.
 %
-In this context, mean field q-learning (Mean-Q)~\cite{DBLP:conf/icml/YangLLZZW18} has been proposed.
-This approach scales well to large numbers of agents and has been successful in various applications. 
+%In this context, mean field q-learning (Mean-Q)~\cite{DBLP:conf/icml/YangLLZZW18} has been proposed.
+%This approach scales well to large numbers of agents and has been successful in various applications. 
 % 
-There are also modern solution which leverages collective abstraction to reduce the complexity of the problem, such as the one proposed in field-informed reinforcement learning~\cite{DBLP:conf/acsos/AguzziVE23}.
+There are also novel solutions which leverage collective abstraction to reduce the complexity of the problem, such as field-informed reinforcement learning~\cite{DBLP:conf/acsos/AguzziVE23}.
 \subsection{Motivation}

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: smaller image

@@
   \centering
-  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
-  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/episode_reward_mean.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/episode_len_mean.pdf}
   \caption{Data collected during training. 
@@
   \centering
-  \includegraphics[width=1\linewidth]{figures/scalability.pdf}
-  \caption{ Communication overhead due to different neighboring strategies.
+  \includegraphics[width=0.8\linewidth]{figures/scalability.pdf}
+  \caption{Communication overhead due to different neighboring strategies.
   }
@@
 \section{Conclusion}\label{sec:conclusion}
-This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE )with performance 
+This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE ) with performance 
  comparable to centralized approaches (i.e., CTDE). 
 %
-These strategies offer the flexibility of DTDE while retaining the stability and performance of CTDE. 
-%
-Specifically, we introduce three approaches, namely: NN Averaging, NN Consensus and Experience Sharing
+Specifically, we introduce three approaches, namely: K-NN averaging, K-NN consensus and experience sharing
  which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
 %
-The results show that two of the three proposed methods significantly enhance DTDE performance, achieving outcomes comparable 
- to CTDE, while NN consensus falls short of this goal, maintaining performance similar to DTDE. 
+The results show that two of the three proposed methods significantly enhance DTDE performance, 
+ achieving outcomes comparable to CTDE, 
+ while NN consensus falls short of this goal,
+  maintaining performance similar to DTDE. 
 %
-Furthermore, we analyzed the communication overhead, demonstrating that it remains minimal across all cases, 
- particularly with experience sharing, making it suitable for scenarios with very limited communication resources.
+Furthermore, we analyzed the communication overhead, 
+ demonstrating that it remains minimal across all cases, 
+ particularly with experience sharing, 
+ making it suitable for scenarios with very limited communication resources.
 

### 2024-10-13 paper-2024-sac-marl-neighbouring-strategies.tex
final pass: improve some aspects of the paper

@@
 \begin{abstract}
-Multi-agent deep reinforcement learning (MADRL) is rapidly emerging as a powerful paradigm for training intelligent agents in complex, multi-agent environments.
+Multi-agent deep reinforcement learning (MADRL) has demonstrated significant potential as a framework for developing autonomous agents capable of operating within complex, multi-agent environments.  
 %
-Extending beyond single-agent reinforcement learning, MADRL enables the development  of both collaborative and competitive agents in several domains, like robotics, traffic management, and video games.
+Extending the single-agent reinforcement learning framework, MADRL enables the development  of both collaborative and competitive agents a wide range of diverse domains, like robotics, traffic management, and video games.
 %
-The most widely adopted training paradigm in MADRL is centralized training with decentralized execution (CTDE), which has demonstrated significant effectiveness. 
+Centralized training with decentralized execution (CTDE) has emerged as the predominant training paradigm, which has demonstrated significant effectiveness in learning complex policies. 
 %
 However, its reliance on a centralized learner necessitates that agents acquire policies offline and subsequently execute them online. 
-This inherent constraint motivates the exploration of decentralized training methodologies.
+This constraint motivates the exploration of decentralized training methodologies.
 %
@@
 %
-In this direction, \emph{reinforcement learning} (RL)~\cite{sutton2018reinforcement} has emerged as a powerful paradigm for training agents that interact with their environment and learn optimal policies through trial and error.
+In this direction, \emph{reinforcement learning} (RL)~\cite{sutton2018reinforcement} has emerged as a prominent paradigm for training agents that interact with their environment and learn optimal policies through trial and error.
 %
@@
 %
-Recent advances in deep learning have further advanced the field, 
+Recent advances in deep learning (DL) have further advanced the field, 
 enabling the training of complex policies in high-dimensional state and action spaces, 
@@
 %
-The goal of each agent is to maximize its cumulative reward. 
+The goal of each agent is to maximize its \emph{cumulative long-term reward}. 
 %
-Environments can be \emph{partially observable}, meaning agents may not have access to the full global state, only receiving local observations through their respective \emph{observation functions}.
+Environments can be \emph{partially observable}, 
+meaning agents may not have access to the full global state, 
+only receiving local observations through their respective \emph{observation functions}.
 
@@
 %In the following, we provide an overview of the key concepts in MARL, 
-%including the formalization of the problem, the deep Q-learning algorithm, and the training paradigms used in the literature.
+%including the formalization of the problem, the Deep Q-Learning algorithm, and the training paradigms used in the literature.
 \subsection{Formalization}
@@
 %
-One of the most popular among these is the Deep Q-learning algorithm.
+One of the most popular among these is the Deep Q-Learning algorithm.
 \subsubsection{Deep Q-Learning Formalization}
-Deep Q-learning~\cite{DBLP:conf/l4dc/FanWXY20} utilizes a deep neural network, 
+Deep Q-Learning~\cite{DBLP:conf/l4dc/FanWXY20} utilizes a deep neural network, 
 often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
@@
 \[ Q^*(s, a) = \mathbb{E}_{s' \sim \mathcal{P}} \left[ r + \gamma \max_{a'} Q^*(s', a') | s, a \right] \]
-
-where $\mathcal{P}$ is the state transition probability distribution.  
-Deep Q-learning aims to train the Q-network to approximate $Q^*(s, a)$ by minimizing the loss function:
+%
+where $\mathcal{P}$ is the state transition probability distribution and $r$ is the immediate reward received after taking action $a$ in state $s$.  
+Deep Q-Learning aims to train the Q-network to approximate $Q^*(s, a)$ by minimizing the loss function:
 
@@
 For centralized training, the global state $s$ can be used as input. 
-The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed Deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
-%For example, in independent Deep Q-learning--more details in \Cref{sec:sota}--each agent updates its Q-network independently using its local reward $r^i$:
+The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed Deep Q-Learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).
+%For example, in independent Deep Q-Learning--more details in \Cref{sec:sota}--each agent updates its Q-network independently using its local reward $r^i$:
 %\begin{equation}
@@
 \begin{enumerate}
-  \item \textit{Offline training:} Agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
-  \item \textit{Online execution:} Agents deploy the learned policy in the environment without further learning.
+  \item \textit{Offline training:} agents interact with a simulator or environment, gathering experience data used to update the central learner's policy.
+  \item \textit{Online execution:} agents deploy the learned policy in the environment without further learning.
 \end{enumerate}
@@
 Unlike CTDE, training and execution phases are not necessarily separate---simultaneous learning and execution allow for adaptation to 
-changing environments or tasks at runtime.
+change environments or tasks at runtime.
 %
@@
 However, DTDE also presents several challenges to overcome, like: 
-i) convergence time is often longer compared to centralized training. 
-ii) The lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions; and 
+i) convergence time is often longer compared to centralized training; 
+ii) the lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions; and 
 iii) online learning in DTDE can introduce non-stationarity if agents do not account for other agents' evolving policies during training, 
@@
 Subsequent work introduced heuristic-based extensions to improve coordination, like distributed Q-learning~\cite{lauer2000algorithm}, hysteretic Q-learning~\cite{matignon2007hysteretic}, lenient Q-Learning~\cite{bloembergen2010lenient}, however empirical comparisons of these algorithms highlight the trade-offs in performance across various MARL tasks and coordination challenges~\cite{matignon2012independent}.
-While initially developed for tabular settings, some of these methods, like hysteretic Q-learning~\cite{palmer2017lenient} and lenient Q-learning, have been extended to deep reinforcement learning settings.
+While initially developed for tabular settings, some of these methods, like hysteretic Q-learning~\cite{palmer2017lenient},
+%and lenient Q-learning, 
+have been extended to deep reinforcement learning settings. 
 However, these independent approaches, even with deep learning, often exhibit instability and slow convergence in complex environments and fundamentally lack explicit mechanisms for inter-agent coordination.
@@
 These strategies leverage local interactions between agents to improve learning efficiency and coordination.
-For this investigation, we focus on deep Q-learning as the underlying learning algorithm,
+For this investigation, we focus on Deep Q-Learning as the underlying learning algorithm,
 and we consider the following strategies: k-nearest neighbor averaging, k-nearest neighbor consensus, and experience sharing.
@@
 $$ \mathcal{N}_k(i) = { j \in N \setminus {i} \mid \text{rank}(d(i,j)) \leq k } $$
-where $\text{rank}(d(i,j))$ denotes the rank of the distance $d(i,j)$ among all distances from agent $i$ to other agents in $N \setminus {i}$, sorted in ascending order (e..g, $\text{rank}(d(i,j)) = 1$ for the smallest distance).
+where $\text{rank}(d(i,j))$ denotes the rank of the distance $d(i,j)$ among all distances from agent $i$ to other agents in $N \setminus {i}$, sorted in ascending order (e.g, $\text{rank}(d(i,j)) = 1$ for the smallest distance).
 Ties can be broken arbitrarily.
@@
 \sloppy
-This approach averages an agent's Q-values with those of its nearest neighbors. 
-Each agent maintains a local Q-network and shares its Q-values with its neighbors. 
+%This approach averages an agent's Q-values with those of its nearest neighbors. 
+In this strategy, each agent maintains a local Q-network and shares its Q-values with its neighbors.
 The neighbors average the received Q-values and use the result to update their own Q-networks. 
-This leverages the collective knowledge of neighboring agents to improve learning.
+This approach allows agents to learn from their neighbors' experiences, potentially improving learning efficiency and coordination.
 %
@@
 %
-In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading eventually to a consensus on the best same policy.
+Instead of directly enforcing a shared policy, 
+we allow each agent to learn independently and periodically select the best-performing agent within its neighborhood as a reference. 
+This approach facilitates decentralized exploration while promoting consensus towards a high-performing policy.
 %
-In this way, each agent $i$ continue to learn independently, but at each iteration, it updates its Q-network using the Q-values of the best-performing agent in its neighborhood.
+Formally, Let $R_i(t)^n$ be the average reward obtained by agent $i$ over the last $n$ episodes, namely
+$R_i(t)^n = \frac{1}{n} \sum_{k=t-n}^{t} r_i(k)$.
+At each time step $t$, 
+each agent $i$ identifies the best-performing neighbor $b_i(t)$ within its $k$-neighborhood $\mathcal{N}_i^k$:
+
+$$b_i(t) = \underset{j \in \mathcal{N}_k(i)}{\operatorname{argmax}} R_j(t)^n$$
 %
-The best performing agent is selected based on the average reward it has received in the last $n$ episodes.
-Formally, the update rule for agent $i$ at time $t+1$ is:
-\begin{equation}
-  \theta^{t+1}_i \leftarrow \theta^t_{\text{best}}
-\end{equation}
-where $\theta^t_{\text{best}}$ is the Q-network of the best-performing agent in the neighborhood $\mathcal{N}_k(i)$ at time $t$.
+Agent $i$ then updates its Q-network parameters $\theta_i$ using the parameters of the best-performing neighbor, namely:
+$\theta_i^{t+1} \leftarrow \theta_{b_i(t)}^t$.
+%
+This process repeats at every consensus update interval.  
+Choosing an appropriate interval balances independent exploration with consensus convergence.
 
@@
 but it also shares a fraction of its experiences with its neighbors.
+%
 This allows agents to learn from each other's experiences, 
@@
 \paragraph{Neighboring-Based Training with Deep Q-Learning}
-The neighboring-based training strategies can be integrated with deep Q-learning to enable distributed learning in multi-agent settings.
+\sloppy
+The neighboring-based training strategies can be integrated with Deep Q-Learning to enable distributed learning in multi-agent settings.
 %
-The algorithm follow the same structure as the deep Q-learning algorithm, 
-but with the addition of the neighboring-based intereactions.
+The algorithm follow the same structure as the Deep Q-Learning algorithm, 
+but with the addition of the neighboring-based interactions.
 %
@@
 depending on the communication overhead and the desired level of coordination.
-
-In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
+%
+In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with Deep Q-Learning.
 \begin{algorithm}
@@
 This section presents the experimental setup and evaluation metrics used to assess the performance of the proposed neighboring-based training strategies.
+%
 All the experiments and data produced are reproducible and publicly available\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.
 \subsection{Simulated environment}
-The proposed multi-agent environment is a variant of the ``gather the items'' scenario, designed to study the impact of neighborhood strategies. 
+The proposed multi-agent environment is a variant of the ``gather the items'' scenario, 
+designed to study the impact of neighborhood strategies. 
 It consists of a 2D Euclidean space populated by $A$ agents and $T$ targets, 
 initially placed at random locations.
-%
-The objective is for the agents to collectively capture all targets, 
-at which point the environment episode terminates successfully.  
+The objective is for the agents to work together to capture all targets, resulting in a successful termination of the environment episode.
 A maximum time limit of $T_{max} = 300$ time steps is enforced to prevent indefinite episodes.
@@
 \begin{itemize}
-  \item \emph{Neighborhood perception}:  Agent $a$ perceives the relative positions (distance and direction) of its $A_v$ nearest neighboring agents. 
+  \item \emph{Neighborhood perception}: an agent $a$ perceives the relative positions (distance and direction) of its $A_v$ (paramers of the environment) the nearest neighboring agents. 
   This information is represented as a set $\mathcal{V}_a^t = \{(d_{aj}^t, \theta_{aj}^t) | j \in \text{Nearest } A_v \text{ agents}\}$, 
   where $d_{aj}^t$ is the Euclidean distance between agent $a$ and agent $j$ at time $t$, and $\theta_{aj}^t$ is the angle between the vector pointing from agent $a$ to agent $j$ and a fixed reference axis.
-  \item \emph{Target perception}: Agent $a$ perceives the relative positions (distance and direction) of its $T_v$ nearest targets. 
+  \item \emph{Target perception}: am agent $a$ perceives the relative positions (distance and direction) of its $T_v$ (parameter of the environment) the nearest targets. 
   This is represented as a set $\mathcal{T}_a^t = \{(d_{ak}^t, \theta_{ak}^t) | k \in \text{Nearest } T_v \text{ targets}\}$, with $d_{ak}^t$ and $\theta_{ak}^t$ defined analogously to the neighborhood perception.
-  \item \emph{Memory}: Agent $a$ maintains a memory $\mathcal{H}_a^t$ of past perceptions, storing the neighborhood and target perceptions from the previous $H_t$ time steps.
+  \item \emph{Memory}: an agent $a$ maintains a memory $\mathcal{H}_a^t$ of past perceptions, storing the neighborhood and target perceptions from the previous $H_t$ time steps.
 Formally, $\mathcal{H}_a^t = \{\mathcal{N}_a^{t-\tau}, \mathcal{T}_a^{t-\tau} | \tau = 1, \dots, H_t\}$.
@@
 Communication between agents is restricted to a neighborhood $\mathcal{C}_a^t \subseteq \mathcal{N}_a^t$ 
-and depends on a communication graph $\mathcal{G}$.
+and depends on a communication graph $\mathcal{G}$ that defines the communication links between agents. In this work, the graph is based on a k-nearest neighbor topology, 
+where each agent communicates with its $k$ (parameter of the simulation) nearest neighbors.
 %
@@
 of neighbor-based decentralized training approaches.
+
 \subsubsection{Reward function}
 In the proposed environment, we design a reward function that both consider the individual performance of each agent (e.g., avoid collision) and the global performance of the team (e.g., collect items in the shortest time possible).
-In the following, we describe the components of the reward function:
-\paragraph{Collisions} Agents are penalized when their action area intersect. This penalty is proportional to the number of agents involved in a collision:
+In the following, we describe the components of the reward function for each agent $a$ at time $t$.
+
+\paragraph{Collisions.} Agents are penalized when their action area intersect. This penalty is proportional to the number of agents involved in a collision:
   \[ \psi = \begin{cases}
@@
 
-\paragraph{Time step} Agents are penalized at each time step by a constant value $\sigma$ defined as
+\paragraph{Time step.} Agents are penalized at each time step by a constant value $\sigma$ defined as
     an hyperparameter, to encourage them to complete the task as quickly as possible.
-    \[ \zeta = - \sigma \]
 
-\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items, discouraging agents from wandering aimlessly.
+\paragraph{Moving towards items.} Each agent $a$ is rewarded if it moves towards one of the visible target items, discouraging agents from wandering aimlessly.
     \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
@@
     $V_{items}$ is the set of visible items.
-\paragraph{Moving away from agents} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
+\paragraph{Moving away from agents.} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
 This strategy encourages agents to avoid clustering and explore the environment more effectively.
@@
 
-\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$ is the set of collected items), 
+\paragraph{Collecting items.} Each agent is rewarded for any collected visible items ($C_i$ is the set of collected items), 
     whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 
-    to develop cooperative behaviors.
-    \[ \rho = 100 \cdot |C_i| \]
+    to develop cooperative behaviors, namely:
+    $\rho = 100 \cdot |C_i|$
 
-\paragraph{Final reward} The final reward is computed as the sum of all the subcomponents:
-  \[ R = \psi + \zeta + \xi + \chi + \rho \]
+\paragraph{Final reward.} The final reward is computed as the sum of all the subcomponents, namely: $ r^a_t = \psi - \sigma + \xi + \chi + \rho $
 
@@
 We ran a total of $42$ training experiments, 
-namely: $6$ different methods %% TODO check how many ex are discussed
+namely: $6$ different methods 
 (centralized, distributed and the three neighbor-based strategies discussed).
@@
 Each experiment consisted of $50$ training episodes. 
+In these episodes, we fix the number of agents to $4$, $A_v = 3$, $T_v = 3$, $H_t = 3$, $k = 2$, $\sigma = 1$ and $\beta = 1$.
+%
+As learning algorithms we employed the Deep Q-Learning algorithm and MAPPO.
+For DQN, we set the discount factor $\gamma = 0.95$, the learning rate $\alpha = 0.001$, the training batch size to $32$.
+Other parameters were set to the default values provided by RLlib. 
+For MAPPO, we used a discount factor of $\gamma = 0.95$, a learning rate of $\alpha = 0.0002$,
+a generalized advantage estimation (GAE) $\lambda = 0.95$, and a training batch size of $2048$, leveraging 20 vectorized environments. All other parameters were set to RLlib's default values
 %
 Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
-  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
+  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions leaving the other parameters fixed.
   In this case, for each experiment we ran $100$ evaluation episodes.
 
-\subsection{Learning algorithm}
-In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
+%\subsection{Learning algorithm}
+%In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
 %
-We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
-  considered in the decision-making process.
+%We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
+%  considered in the decision-making process.
 %
-A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
-  for long-term benefits, striking a balance between short-term and long-term planning.
+%A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
+%  for long-term benefits, striking a balance between short-term and long-term planning.
 %
-We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
+%We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
 %
-This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
-  the training process, specially in complex environments with multiple interacting agents.
+%This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
+%  the training process, specially in complex environments with multiple interacting agents.
 %
-For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
-  of experiences in each update. 
+%For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
+%  of experiences in each update. 
 %
-A smaller batch size could lead to noisier updates, while a larger one might slow down training without
-  significantly improving performance.
+%A smaller batch size could lead to noisier updates, while a larger one might slow down training without
+%  significantly improving performance.
 %
@@
 It provides insights into the agent's efficiency in completing tasks, especially in environments 
-  where shorter episodes indicate better performance.
-%
-The mean episode length $L_{mean}$ is calculated as:
+  where shorter episodes indicate better performance. Formally:
 \[ L_{mean} = \frac{1}{N} \sum_{i=1}^{N} L_i \]
@@
 %
-This difference becomes even more evident when considering the Mean Episode Length metric, where CTDE not only converges 
+This difference becomes even more evident when considering the $L_{mean}$, where CTDE not only converges 
  faster but also solves the task using shorter episodes than DTDE.

### 2024-10-13 paper-2024-sac-marl-neighbouring-strategies.tex
final pass: complete

@@
   \centering
-  \includegraphics[width=0.7\linewidth]{figures/behavior.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/behavior.pdf}
   \caption{Examples of cooperative and uncoordinated behavior.
@@
 Regarding the proposed neighbor-based approaches, it can be observed that both \emph{experience sharing} and 
- \emph{NN averaging} enhance the performance of DTDE, achieving results comparable to CTDE while also increasing 
+ k-NN averaging enhance the performance of DTDE, achieving results comparable to CTDE while also increasing 
  learning stability. 
 % 
-On the other hand, \emph{NN consensus} maintains performance levels similar to DTDE, which may be attributed to the 
+On the other hand, k-NN consensus maintains performance levels similar to DTDE, which may be attributed to the 
  simplicity of the implemented consensus policy. 
@@
  of agents -- specifically to 8, 16, and 32 -- and measuring the time required to complete the task 
- (i.e., mean episode length).
+ (i.e., $L_mean$).
 
@@
 %
-In contrast, CTDE, NN averaging, and experience sharing maintain strong performance. 
+In contrast, CTDE, k-NN averaging, and experience sharing maintain strong performance. 
 %
-Similar to the training phase, NN consensus does not achieve the same results as the other two neighbor-based 
+Similar to the training phase, k-NN consensus does not achieve the same results as the other two neighbor-based 
  approaches but remains on par with DTDE in terms of performance.
-
 \paragraph{Communication overhead}
 
-The proposed neighbor-based approaches, particularly NN averaging and experience sharing, achieve performance
+The proposed neighbor-based approaches, particularly k-NN averaging and experience sharing, achieve performance
  comparable to CTDE while maintaining a decentralized learning structure similar to DTDE. 
 % 
-However, this entails a communication overhead due to the information agents must exchange with their neighbors
+However, this entails a communication overhead at runtime due to the information agents must exchange with their neighbors
  -- see \Cref{fig:scalability}. 
 %
-For NN consensus, the overhead remains constant, as each agent selects the best neighbor and only exchanges 
- information with that agent, meaning the amount of data shared does not increase with the number of neighbors. 
+For k-NN consensus, the overhead remains constant, as each agent selects the best neighbor and only exchanges 
+ information with that agent, 
+ meaning the amount of data shared does not increase with the number of neighbors. 
 % 
-In contrast, for NN averaging and experience sharing, the overhead scales linearly. 
+In contrast, for k-NN averaging and experience sharing, the overhead scales linearly. 
 %
@@
 %
-For NN averaging, however, this increase is more significant, as even a moderately complex neural network 
+For k-NN averaging, however, this increase is more significant, as even a moderately complex neural network 
  has a substantially larger memory footprint.
@@
 This makes all approaches feasible, although in scenarios with limited communication resources, experience 
- sharing would be the optimal choice, as it provides performance similar to NN averaging but with 
+ sharing would be the optimal choice, as it provides performance similar to k-NN averaging but with 
  much lower overhead.
-
 % \begin{itemize}
@@
   \includegraphics[width=0.8\linewidth]{figures/episode_len_mean.pdf}
-  \caption{Data collected during training. 
-  We can see that two of the three neighbor-based strategies achieve performance similar to CTDE.
+  \caption{Training performance of neighbor-based decentralized training strategies compared to centralized (CTDE) and fully decentralized (DTDE) approaches. 
+  Two of the three neighbor-based methods achieve performance comparable to CTDE, 
+  demonstrating the effectiveness of these methods in achieving scalability and coordination.
   }
@@
   \end{subfigure}
-  \caption{ Data collected during evaluation.
-  We can see how, increasing the number of agents, the DTDE methods become more unstable and takes more 
-  steps to solve the task, while neighbor-based strategies maintain -- on average -- results comparable to CTDE.
+  \caption{Scalability comparison of training methods in the evaluation phase.
+  DTDE performance degrades with increasing agent numbers, 
+  while CTDE and neighbor-based methods maintain comparable efficiency.
   }
@@
   \includegraphics[width=0.8\linewidth]{figures/scalability.pdf}
-  \caption{Communication overhead due to different neighboring strategies.
+  \caption{Communication overhead (in MB) for different neighboring strategies as a function of the number of neighbors.
   }
@@
 This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE ) with performance 
- comparable to centralized approaches (i.e., CTDE). 
+ comparable to centralized approaches (i.e., CTDE) therefore enabling online adaptation.
 %
-Specifically, we introduce three approaches, namely: K-NN averaging, K-NN consensus and experience sharing
+Specifically, we discuss three approaches, namely: k-NN averaging, k-NN consensus and experience sharing
  which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
@@
 \begin{enumerate*}[label=(\roman*)]
-  \item explore the implementation of more advanced consensus algorithms to determine if this strategy can also achieve 
+  \item explore the implementation of more advanced consensus algorithms (e.g., deep QD-learning) to determine if this strategy can also achieve 
    results comparable to the other two;
   \item develop more sophisticated communication protocols to further reduce communication overhead; and
-  \item test these approaches in a wider range of, and more complex, scenarios than the one considered in this paper.
+  \item test these approaches in a wider range and more complex scenarios than the one considered in this paper (e.g., vectorized multi-agent environment~\cite{bettini2022vmas}).
 \end{enumerate*}

### 2024-10-13 paper-2024-sac-marl-neighbouring-strategies.tex
better fig 1

@@
   \includegraphics[width=0.49\linewidth]{figures/DTDE.pdf}
-  \caption{Graphical representation of CTDE (left) and DTDE (right) in MARL.}
+  \caption{Graphical representation of CTDE (left) and DTDE (right) in MARL.
+  For simplicity, only two agents are represented. However, the model can easily be extended to the general case of N agents.}
   \label{fig:learning_paradigms}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{figures/behavior.pdf}
+  \includegraphics[width=0.7\linewidth]{figures/behavior.pdf}
   \caption{Examples of cooperative and uncoordinated behavior.
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{figures/episode_reward_mean.pdf}
-  \includegraphics[width=0.8\linewidth]{figures/episode_len_mean.pdf}
+  \includegraphics[width=0.75\linewidth]{figures/episode_reward_mean.pdf}
+  \includegraphics[width=0.75\linewidth]{figures/episode_len_mean.pdf}
   \caption{Training performance of neighbor-based decentralized training strategies compared to centralized (CTDE) and fully decentralized (DTDE) approaches. 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{figures/scalability.pdf}
+  \includegraphics[width=0.7\linewidth]{figures/scalability.pdf}
   \caption{Communication overhead (in MB) for different neighboring strategies as a function of the number of neighbors.
